---
title: "TOUCH-BRAIN: Pre-Registration Plan"
author: "Phuc TU Nguyen"
date: "2025-06-06"

output:
  html_document:
    theme: flatly       
    highlight: tango     # Nice syntax highlighting for R code
    toc: true
    toc_depth: 3
    toc_float: 
      collapsed: false   # Keeps the TOC expanded
      smooth_scroll: true
    number_sections: true
    code_folding: hide   
    df_print: paged      # Makes large data frames look like neat tables
---

```{r setup, warning=FALSE, echo=FALSE, message=FALSE}
## Set up libraries and define paths with function

rm(list = ls())
library(rstudioapi)

script_path <- dirname(rstudioapi::getActiveDocumentContext()$path)
function_path <- file.path(script_path, "function")

source(file.path(function_path, "loadconfig.R"))
load_lib()
load_path(script_path)
load_palette()

phases <- c(
  "Movement Cue",
  "Before Movement",
  "During Movement",
  "Early Movement", "Half Movement", "Late Movement", "Full Movement",
  "After Movement"
)
vps <- c("P")
power.type <- c("raw", "log")[1] # change the format of Beta power here
predictor.name <- ifelse(power.type == "log", "Power Log-Ratio", "Power Difference")
```


# Pool and preprocess data

Behavioral and EEG data are merged across all participants and blocks. Block number and trial number are assigned per condition (t/m &times; a/p &times; unimodal/self-touch)

```{r Pool beh, warning=FALSE, message=FALSE, echo=FALSE}
source(file.path(function_path, "loaddata.R"))

beh_combined_df <- load_behdata(vps, pathlist$beh_data_path)
beh_combined_df <- adjust_beh_df(beh_combined_df)
# Test for sufficient blocks
beh_test <- beh_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial_beh = n(), .groups = "drop")
```

```{r Pool eeg, warning=FALSE, message=FALSE, echo=FALSE}
eeg_combined_df <- load_eegdata(vps, file.path(pathlist$eeg_data_path, "Revise_5Phase_Strict7s"))

# Adjustment according to protocol
{
  empty_row <- eeg_combined_df[1, ]
  empty_row[1, ] <- NA

  empty_row$filename <- "P23_move_active_results.xls"
  eeg_combined_df <- rbind(
    eeg_combined_df[1:(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[36]), ],
    empty_row,
    eeg_combined_df[(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[37]):nrow(eeg_combined_df), ]
  )
  eeg_combined_df <- eeg_combined_df[-which(eeg_combined_df$filename == "P23_move_passive_results.xlsx")[51], ]
}


eeg_combined_df <- adjust_eeg_df(eeg_combined_df)


# Test for sufficient blocks
eeg_test <- eeg_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial = n(), .groups = "drop")

# Compare trial counts between behavioral and EEG data
testmerge <- left_join(beh_test, eeg_test,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal")
) %>%
  arrange(NAME, unimodal, QUESTION, ACTIVE) %>%
  mutate(trialdiff = ntrial_beh - ntrial)
```

```{r Merge beh and eeg data, warning=FALSE, message=FALSE, echo=FALSE}
# Merge full behavioral and EEG datasets
merge_df <- left_join(beh_combined_df, eeg_combined_df,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal", "trial_number")
)

# Compare trial counts between behavioral and EEG data
testmerge1 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())
```

```{r Remove data, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# Remove specific blocks for specific subjects
merge_df <- merge_df %>%
  filter(!(NAME == "P03" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "p" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P17" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P22" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P23" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "p" & trial_number %in% c(50))) %>%
  filter(!(NAME == "P25" & !is.na(unimodal) & unimodal == "1" & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(1))) %>%
  # temporary filter due to unsatisfactory preprocessing
  filter(!(NAME %in% c("P11", "P17", "P22")))

testmerge2 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

testmerge3 <- merge_df %>%
  mutate(
    NAME = str_extract(NAME, "\\d+") %>% as.numeric(),
    unimodal = case_when(
      unimodal %in% c("1", "2") ~ "Unimodal",
      !unimodal %in% c("1", "2") ~ "Self-touch"
    ),
    QUESTION = case_when(
      QUESTION == "t" ~ "Judge Touch",
      QUESTION == "m" ~ "Judge Move"
    ) %>% factor(levels = c("Judge Touch", "Judge Move")),
    ACTIVE = case_when(
      ACTIVE == "a" ~ "Active",
      ACTIVE == "p" ~ "Passive"
    ) %>% factor(levels = c("Passive", "Active"))
  ) %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

ggplot(testmerge3) +
  geom_point(aes(x = NAME, y = n, color = unimodal)) +
  facet_wrap(QUESTION ~ ACTIVE) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  scale_color_discrete("Condition") +
  labs(
    title = "Check for data completeness - Before Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )


demogr_df <- read_xlsx(file.path(pathlist$demogr_data_path, "demographic.xlsx"))
merge_df <- left_join(merge_df, demogr_df, by = "NAME")

test <- merge_df %>% filter(is.na(unimodal))
```

```{r Save merged data, warning=FALSE, message=FALSE, echo=FALSE}
# Export merged data to Excel
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
write_xlsx(merge_df, file.path(pathlist$result_path, xlsx_name))
# print(codebookr::codebook(rawData), file.path(pathlist$result_path,"ST_EEG_Codebook.docx"))

rm(list = c(
  "demogr_df",
  "beh_combined_df", "beh_test",
  "eeg_combined_df", "eeg_test",
  "empty_row",
  "merge_df",
  ls(pattern = "^test")
))
```


```{r Read from csv, warning=FALSE, message=FALSE, echo=FALSE}
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
source(file.path(function_path, "preprocessdata.R"))
# channels <- expand.grid(c("F", "Fc", "FC", "C", "CP", "P"), c("3", "5", "z", "4", "6"))
channels <- expand.grid(c("C"), c("3", "4"))
channels <- paste0(channels$Var1, channels$Var2)
```

**Target Length**: based on the task type (touchLength or movLength is selected).

**Gain/Flipped Gain**: 1 = Unity (move=touch), 2 = NonUnity, incl Move > Touch and Move < Touch.

**Condition Labels (condN)**: (1) Self-touch Active - Judge Touch, 
(2) Self-touch Passive - Judge Touch, 
(3) Self-touch Active - Judge Move, 
(4) Self-touch Passive - Judge Move*, 
(5) Unimodal - Judge Touch, 
(6) Unimodal Active - Judge Move, 
(7) Unimodal Passive - Judge Move. 

**Flipped Gain**: Calculated as $|\frac{TargetLength}{InterferenceLength}\ |$.        **Absolute Error**: Calculated as $|\frac{ReportedLength}{TargetLength}\ - 1|$.

```{r Preprocess data, layout="l-body-outset", fig.width=4, fig.height=4, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
options(width = 500)

rawData <- read_excel(path = file.path(pathlist$result_path, xlsx_name))
rawData <- preprocess_beh_df(rawData) %>%
  select(
    sbjN, Gender, trialN, task, mov, unimodal, condN, BLOCK, trial_number, DURATION, MovDur, HalfDur,
    gain, flipped.gain, touchLength, movLength, Target_length, Interference_length, resp, estError, absError, delta,
    ExclCode,
    starts_with(channels)
  )

rawData %>%
  select(
    sbjN, condN, BLOCK, trialN, flipped.gain, Target_length, Interference_length, resp,
    matches("^(C3|C4).*_(pre|full|early|late)$")
  ) %>%
  arrange(sbjN, condN, BLOCK, trialN) %>%
  rmarkdown::paged_table(options = list(rows.print = 5, cols.print = 10))
```


# Removing outliers

Idea: Extreme slow or quick movement could be excluded because participants pressed arrows too quick and submitted responses immediately.

```{r Filter abnormal movement, fig.width=12, fig.height=5, echo=TRUE, warning=FALSE, message=FALSE}
# Calculate IQR boundaries for MovDur
q1 <- quantile(rawData$MovDur, 0.25, na.rm = TRUE)
q3 <- quantile(rawData$MovDur, 0.75, na.rm = TRUE)
iqr_val <- q3 - q1
upper_iqr_limit <- q3 + (1.5 * iqr_val)
lower_iqr_limit <- q1 - (1.5 * iqr_val)

# Create a summary table
exclusion_check <- rawData %>%
  summarise(
    Total_Trials = n(),
    Missing_Dur = sum(is.na(MovDur)), # due to EEG analyses: epoch rejection or movement longer than 8s
    Outliers_IQR_High = sum(MovDur > upper_iqr_limit, na.rm = TRUE), # movement too slow
    Outliers_IQR_Low = sum(MovDur < lower_iqr_limit, na.rm = TRUE) # movement to quick
  )

# Print summary
cat(sprintf(
  "%d/%d trials removed: %.2f%%\n",
  exclusion_check$Missing_Dur,
  exclusion_check$Total_Trials,
  100 * (exclusion_check$Missing_Dur) / exclusion_check$Total_Trials
))

# Which participants have missing MovDur
(rawData %>%
  filter(is.na(MovDur)) %>%
  count(sbjN, condN, ExclCode))

rawData <- rawData %>%
  filter(!is.na(MovDur))

p1 <- ggplot(rawData) +
  geom_histogram(aes(x = MovDur)) +
  scale_x_continuous("Move Duration (s)", limits = c(0, 10), breaks = seq(0, 20, 10)) +
  labs(title = "Distribution of Moving Duration (excluded: more than 6.8 s)")
summary(rawData$MovDur)
p1
```



Extreme responses at both end (too large or too small estimation) are excluded because participants pressed arrows too quick and submitted responses immediately.


```{r Filter extreme responses, fig.width=12, fig.height=5, echo=TRUE, warning=FALSE, message=FALSE}
# Make long data
filter.choice <- list(
  "puffer", # extreme responses across all participants
  "sbjN" # extreme responses of each participant
)

rawData.filter <- filter_outliers(
  df = rawData %>% mutate(puffer = 1 %>% as.factor()),
  value_col = "estError", group_cols = filter.choice[[2]]
) # filter extreme response
ggplot(rawData) +
  geom_histogram(aes(x = 100 * estError)) +
  scale_x_continuous("Estimation Error (%)", limits = c(-150, 300)) +
  labs(title = "Response distribution before filtering out outliers")
ggplot(rawData.filter) +
  geom_histogram(aes(x = 100 * estError)) +
  scale_x_continuous("Estimation Error (%)", limits = c(-150, 300)) +
  labs(title = "Response distribution after filtering out outliers")

# --- Calculate Data Loss ---
# Print summary
cat(sprintf(
  "%d/%d trials removed: %.2f%%\n",
  nrow(rawData) - nrow(rawData.filter),
  nrow(rawData),
  100 * (nrow(rawData) - nrow(rawData.filter)) / nrow(rawData)
))

# Identify which conditions are losing the most data
(loss_report <- rawData %>%
  anti_join(rawData.filter, by = c("sbjN","condN", "BLOCK","trial_number")) %>%
  count(condN, name = "excluded_count"))
```

Extreme Beta power values at both end (too large or too small) are filtered out at both end. 

**Idea: (1) Filter out the extreme large values. (2) Log transform for skewed data**

```{r Filter extreme beta power values, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
filter.choice <- list(
  "puffer", # extreme responses across all participants
  "sbjN", # extreme responses of each participant
  c("sbjN", "channellocation_timing") # filter extreme Beta power values by participant and electrode position and timing
)
longrawData <- long_beh_eeg_df(rawData.filter)

# raw data require filtering outliers
longData <- filter_outliers(df = longrawData, value_col = "powerBeta", group_cols = filter.choice[[3]])


ggplot(longrawData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5) +
  facet_wrap(~timing) +
  scale_x_continuous(expression(paste("Beta Power", " power (", mV^2, ")"))) +
  scale_y_continuous(limits = c(0, 2000)) +
  labs(title = "Distribution of Raw Beta Power before filtering out outliers")
ggplot(longData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5) +
  facet_wrap(~timing) +
  scale_x_continuous(expression(paste("Beta Power", " power (", mV^2, ")"))) +
  scale_y_continuous(limits = c(0, 2000)) +
  labs(title = "Distribution of Raw Beta Power after filtering out outliers")

if (power.type == "log") {
  longData <- longData %>%
    mutate(across(starts_with(c("powerBeta")), ~ 10 * log10(.x))) # log-transformation

  ggplot(longData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5) +
  facet_wrap(~timing) +
  scale_x_continuous(expression(paste("Beta Power (dB)"))) +
  scale_y_continuous(limits = c(0, 2000)) +
  labs(title = "Distribution of Log-Transformed Beta Power after filtering out outliers")
  }



shortData <- short_beh_eeg_df(longData %>% select(sbjN:powerBeta)) %>%
  mutate(unimodal = as.factor(unimodal))

testmerge4 <- shortData %>%
  mutate(sbjN = str_extract(sbjN, "\\d+") %>% as.numeric()) %>%
  group_by(sbjN, task, mov, unimodal) %>%
  summarise(n = n()) %>%
  mutate(remain_percent = case_when(
    unimodal == "Self-touch" ~ n / 54,
    unimodal == "Unimodal" ~ n / 36
  ))

ggplot(testmerge4) +
  geom_point(aes(x = sbjN, y = n, color = unimodal)) +
  facet_wrap(task ~ mov) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  scale_color_discrete("Condition") +
  labs(
    title = "Check for data completeness - After Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )
# --- Calculate Data Loss ---
# Identify which conditions are losing the most data
(loss_report <- rawData.filter %>%
  anti_join(shortData, by = c("sbjN", "trial_number", "condN", "BLOCK")) %>%
  count(condN, name = "excluded_count"))

cat(sprintf(
  "%d/%d trials removed: %.2f%%\n",
  sum(loss_report$excluded_count),
  nrow(rawData.filter),
  100 * sum(loss_report$excluded_count) / nrow(rawData.filter)
))


# To calculate change of Beta power
# present data frame_ one column for C3, one column for C4
parData <- longData %>%
  select(sbjN:delta, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

byBaseline.shortData <- shortData %>%
  select(sbjN:absError, starts_with("C3"), starts_with("C4"))


if (power.type == "raw") {
  byBaseline.shortData <- byBaseline.shortData %>%
    rowwise() %>%
    # For raw data:
    mutate(
      C3_full = 100 * (C3_full - C3_pre) / C3_pre,
      C4_full = 100 * (C4_full - C4_pre) / C4_pre,
      C3_early = 100 * (C3_early - C3_pre) / C3_pre,
      C4_early = 100 * (C4_early - C4_pre) / C4_pre,
      C3_late = 100 * (C3_late - C3_pre) / C3_pre,
      C4_late = 100 * (C4_late - C4_pre) / C4_pre
    ) %>%
    mutate(C3_pre = 0, C4_pre = 0)
}

if (power.type == "log") {
  byBaseline.shortData <- byBaseline.shortData %>%
    rowwise() %>%
    # For Decibels (Log) data
    mutate(
      C3_full = (C3_full - C3_pre),
      C4_full = (C4_full - C4_pre),
      C3_early = (C3_early - C3_pre),
      C4_early = (C4_early - C4_pre),
      C3_late = (C3_late - C3_pre),
      C4_late = (C4_late - C4_pre)
    ) %>%
    mutate(C3_pre = 0, C4_pre = 0)
}

byBaseline.longData <- long_beh_eeg_df(byBaseline.shortData)

# Create a unique trial ID in both datasets
longData <- longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

byBaseline.longData <- byBaseline.longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

# Filter byBaseline.longData to keep only rows present in longData - remove outliers based off the raw power Beta
byBaseline.longData <- byBaseline.longData %>%
  filter(trialID %in% longData$trialID)


byBaseline.parData <- byBaseline.longData %>%
  select(sbjN:absError, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

rm(list = c(ls(pattern = "raw|test")))
```


# Participants
```{r Demographics, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Sex distribution
shortData %>%
  distinct(sbjN, Gender) %>%
  group_by(Gender) %>%
  summarise(n = n()) %>%
  mutate(per = n / sum(n)) %>%
  ggplot() +
  geom_col(aes(x = Gender, y = 100 * per, fill = Gender), show.legend = F) +
  labs(
    title = "Participant - Sex",
    x = "Sex", y = "Percentage (%)"
  ) +
  theme(
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )
```


# Behavioral results

```{r Behavioral Plots, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Subject-level aggregation
plotData <- shortData %>%
  group_by(sbjN, task, mov, unimodal, gain, Target_length) %>%
  summarise(response = mean(resp), .groups = "drop") %>%
  group_by(task, mov, unimodal, gain, Target_length) %>%
  summarise(
    mean = mean(response),
    se = sd(response) / sqrt(n()), # SE across subjects
    n = n(),
    .groups = "drop"
  )

# Plot
p1 <- ggplot(data = plotData %>% filter(unimodal == "Self-touch")) +
  geom_point(aes(x = Target_length, y = mean, color = gain), show.legend = F) +
  geom_line(aes(x = Target_length, y = mean, color = gain, group = gain), show.legend = F) +
  geom_ribbon(aes(
    x = Target_length, ymin = mean - se, ymax = mean + se,
    fill = gain, group = gain
  ), alpha = 0.15, show.legend = F) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(task ~ mov) +
  scale_x_continuous(limits = c(2, 10), breaks = seq(4, 8, by = 2)) +
  scale_y_continuous(limits = c(2, 10), breaks = seq(2, 10, by = 2)) +
  labs(
    title = "Self-touch Conditions",
    x = "Actual target extent (cm)", y = "",
    color = "Gain", fill = "Gain"
  ) +
  theme(
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )

p2 <- ggplot(data = plotData %>% filter(unimodal == "Unimodal")) +
  geom_point(aes(x = Target_length, y = mean, color = gain), show.legend = T) +
  geom_line(aes(x = Target_length, y = mean, color = gain, group = gain), show.legend = T) +
  geom_ribbon(aes(
    x = Target_length, ymin = mean - se, ymax = mean + se,
    fill = gain, group = gain
  ), alpha = 0.15, show.legend = T) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(task ~ mov, drop = T) +
  scale_x_continuous(limits = c(2, 10), breaks = seq(4, 8, by = 2)) +
  scale_y_continuous(limits = c(2, 10), breaks = seq(2, 10, by = 2)) +
  labs(
    title = "Unimodal Conditions",
    x = "Actual target extent (cm)", y = "Perceived target extent (cm)",
    color = "Gain", fill = "Gain"
  ) +
  theme(
    legend.position = c(.15, .9),
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.key = element_blank(),
    legend.background = element_rect(fill = "transparent"),
    legend.title = element_text(size = 16)
  )

grid.arrange(p2, p1, ncol = 2)
```

## Calculate Interference Coefficients
```{r ICs, fig.height= 4, fig.width= 7, warning=FALSE, message=FALSE, collapse = TRUE}
w <- shortData %>%
  filter(unimodal == "Self-touch") %>%
  # filter(gain != 1.25, gain != 0.8)  %>%
  group_by(sbjN, mov, task) %>%
  do({
    model <- lm(resp ~ 0 + touchLength + movLength, data = .)
    as.data.frame(t(coef(model)))
  }) %>%
  ungroup() %>%
  mutate(
    normTouch = touchLength / (movLength + touchLength),
    normMove = movLength / (movLength + touchLength),
    weights = case_when(
      task == "Judge Touch" ~ normMove,
      task == "Judge Movement" ~ normTouch
    )
  )

w$mov <- factor(w$mov, levels = c("Active", "Passive"))

wideW <- w %>%
  select(-c(touchLength, movLength, normTouch, normMove)) %>%
  pivot_wider(
    names_from = c(task, mov), # Columns to use for names
    values_from = c(weights), # Values to fill in the table
    names_sep = "_"
  )
# clipr::write_clip(wideW)

ggplot(w, aes(x = mov, y = weights, fill = interaction(mov, task))) +
  geom_bar(stat = "summary", show.legend = FALSE) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  facet_wrap(~task) +
  ylim(0, 1) +
  labs(
    x = "Condition",
    y = "Weigt of task-irrelevant information (ω)",
    title = "Mean Interference Weights (ω) \nAcross Movement and Judgment Conditions"
  ) +
  theme(
    aspect.ratio = 2,
    legend.position = "bottom",
    strip.text = element_text(size = 10),
    plot.title = element_text(size = 13),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12)
  )
```

## Run ANOVA
```{r Behavioral ANOVA, warning=FALSE, message=FALSE, collapse = TRUE}
full_ANOVA <- aov_ez(
  id = "sbjN",
  dv = "weights",
  within = c("mov", "task"),
  data = w,
  anova_table = list(correction = "GG", es = "pes") # request partial eta squared
)

# Use nice() to display the ANOVA table with effect sizes:
nice(full_ANOVA)
```

# EEG results
## Variable definition

  - **Estimation Error** quantifies *perceptual interference* with both positive and negative value, i.e., overestimation and negative estimation, respectively.
  
  $$estError = \frac{reported length}{target length}\ - 1$$
  
  - **ABSOLUTE Estimation Error** quantifies *perceptual interference* without negative value, i.e., the degree to which the perceptual judgement deviates from the target (true) value OR how much the perceptual judgement is interfered by other information.
  
  $$|estError| = |\frac{reported length}{target length}\ - 1|$$
  
  - **Beta Power Difference** between the left hemisphere (C3) and the right hemisphere (C4) represents the degree to which motor activity interferes with tactile processing. Positive difference implies weaker interference of motor information (tactile focus), while negative difference implies stronger interference of motor information (motor focus).
  
  $$\Delta{B} = B_{C3} - B_{C4}$$
  

Because movement and tactile spatial percepts during self-touch are interfered by the processing of tactile and movement information, respectively, we expect that the neural marker of these two components could be used to predict judgement accuracy. For example, a negative difference in beta power between C3 and C4 *(C3 - C4)* reflects larger processing of motor information relative to tactile information and may suggest that motor information is weighted more in movement judgement than touch judgement

<p style="text-align: justify;">

## ERD variability

Check for ERD/S: Relative to the baseline (before movement), we see a drop (ERD) in beta power amplitude in early movement and a rebound (ERS) after movement stops (after movement).

```{r ERD Plots, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
plotData <- longData %>%
  filter(unimodal == "Unimodal" & timing != "Full Movement") %>%
  group_by(condN, timing, relativehemisphere, location) %>%
  get_summary_stats(powerBeta)
# summarise(powerBeta=mean(powerBeta))

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN), size = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), size = 1) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), size = 2) +
  facet_wrap(~relativehemisphere) +
  scale_color_manual("Condition", values = palette$three.color2) +
  labs(
    title = "Beta Power in unimodal conditions at contra-lateral hemisphere",
    x = "Movement Phases",
    # y = expression(paste("x axis ", ring(A)^2)),
    y = expression(paste("Averaged ", Beta, " power (", mV^2, ")"))
  ) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )


plotData <- byBaseline.longData %>%
  filter(unimodal == "Unimodal" & timing != "Full Movement") %>%
  group_by(condN, timing, relativehemisphere, location) %>%
  get_summary_stats(powerBeta)

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN), size = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), size = 1) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), size = 2) +
  facet_wrap(~relativehemisphere) +
  scale_color_manual("Condition", values = palette$three.color2) +
  labs(
    title = "Beta ERD in unimodal conditions at contra-lateral hemisphere",
    x = "Movement Phases",
    y = "Relative Power Change (%)"
  ) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )
```




## Self-touch: Interhemispheric interference
**Does the relative difference in beta power between channel C3 and C4 during self-touch explain the asymmetrical, bidirectional interference of movement and tactile spatial percepts?**

H: Negative difference in the beta power between the channels C3 and C4 [C3-C4] (i.e., stronger motor processing than tactile processing) is associated with smaller error in move judgement and larger error in touch judgement.

### Model 1A: Does interhemispheric balance predict how accurate participants are around the target?

We fit a linear mixed-effects model of the fixed effects including 

- [1] **interhemispheric balance**: trial-level difference in beta power between C3 and C4 electrodes. A positive difference is associated with a focus on tactile processing, and a negative difference is associated with stronger motor processing 

- [2] **task**: Judge Touch (reference) vs Judge Movement

- [3] **movement type**: Passive (reference) vs Active]

- [4] **non-unity gain**: Move < Touch (i.e., 1:1.5, reference) vs Move > Touch (i.e., 1.5:1) 

To account for repeated measures within participants, we included a random intercept for subject.

```{r Model 1A, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
filter.timing <- "Full"
predictData <- parData %>%
  filter(flipped.gain != "1.Unity" & unimodal == "Self-touch" & timing == paste(filter.timing, "Movement")) %>%
  mutate(sbjN = factor(sbjN)) %>%
  mutate(
    estError = (resp - Target_length) / Target_length,
    GAIN = flipped.gain
  )

# CODING APPROACH 1: DUMMY CODING
# 1. Set Passive as the Reference
# Assuming "Passive" is the first (reference) level
predictData$mov <- relevel(predictData$mov, ref = "Passive")
(contrasts(predictData$mov) <- contr.treatment(2))

# 2. Set Touch as reference
(contrasts(predictData$task) <- contr.treatment(2))

# 3. Set Gain contr.treatment(2)
predictData$gain <- factor(predictData$gain, levels = c("Move < Touch", "Move > Touch"))
(contrasts(predictData$gain) <- contr.treatment(2))

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov * gain + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
summary_df <- as.data.frame(summary(model)$coefficients) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  rownames_to_column("factor") %>%
  mutate(factor = factor %>%
    str_replace_all("PowerDiff", predictor.name) %>%
    str_replace_all("task1", "Task [JudgeTouch]") %>%
    str_replace_all("task2", "Task [JudgeMove]") %>%
    str_replace_all("mov1", "Movement [Passive]") %>%
    str_replace_all("mov2", "Movement [Active]") %>%
    str_replace_all("gain1", "Gain [M<T]") %>%
    str_replace_all("gain2", "Gain [M>T]") %>%
    str_replace_all(":", " × "))

xlsx::write.xlsx(
  x = summary_df %>%
    mutate(across(where(is.numeric), ~ format(.x, decimal.mark = "."))),
  sheetName = "p1A_lmer",
  file = file.path(
    pathlist$result_path,
    paste0("lmer_results_", power.type, ".xlsx")
  ), append = TRUE
)

# Generate predictions for PowerDiff across task, mov, and gain
pred <- ggpredict(model, terms = c("PowerDiff [all]", "task", "mov", "gain"))

# # Comment PHUC: Wrong plot? Does geom_smooth lm does the same thing as lmer()?
# ggplot(
#   predictData,
#   aes(x = PowerDiff, y = estError, color = task)
# ) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   geom_vline(xintercept = 0, linetype = "dashed") +
#   geom_point(alpha = .05, show.legend = F) +
#   geom_smooth(method = "lm", show.legend = T) +
#   labs(
#     title = "Predicting Judgement Error with Difference of Beta Power",
#     x = "Beta Power Difference: C3 - C4",
#     y = "Judgement Error\n(both Over and Underestimation)"
#   ) +
#   scale_color_manual("Task", values = palette$two.color1) +
#   scale_x_continuous(limits = c(-6.5, 5.5)) +
#   scale_y_continuous(limits = c(-1, 2.5)) +
#   facet_grid(gain ~ mov) +
#   theme(
#     aspect.ratio = 1,
#     legend.position = "bottom",
#     strip.text = element_text(size = 16),
#     panel.spacing = unit(1, "lines"),
#     plot.title = element_text(size = 19),
#     axis.text = element_text(size = 18),
#     axis.title = element_text(size = 18)
#   )
x_axis <- ifelse(power.type == "raw",
  expression(paste("Beta Power Difference", " power (", mV^2, ")")),
  ifelse(power.type == "log",
    expression(paste("Beta Power Log-Ratio (dB)"))
  )
)
# Plot predictions
p0 <- ggplot(pred, aes(x = x, y = predicted, color = group)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  annotate("text", x = -.5, y = +Inf, label = sprintf("\u2190\u2190\u2190\nmotor-focused"), color = palette$two.color1[2], hjust = 1, vjust = "top", size = 12 / .pt) +
  annotate("text", x = +.5, y = +Inf, label = sprintf("\u2192\u2192\u2192\ntactile-focused"), color = palette$two.color1[1], hjust = 0, vjust = "top", size = 12 / .pt) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2) +
  facet_grid(panel ~ facet) + # Adjust based on ggpredict output (mov × gain)
  labs(
    title = paste("Predicting Judgement Error with Beta Power during", filter.timing, "Self-touch"),
    subtitle = paste0("Beta", predictor.name," x Task x Movement type x Gain"),
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(-1 = underestimation, 0 = accurate, +1 =overestimation)\n"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_fill_manual("Task", values = palette$two.color1) +
  theme(
    aspect.ratio = 1,
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
p0

(anova.model <- anova(model))
rownames(anova.model) <- rownames(anova.model) %>%
  str_replace_all("PowerDiff", predictor.name) %>%
  str_replace_all("task", "Task") %>%
  str_replace_all("mov", "Movement") %>%
  str_replace_all("gain", "Gain") %>%
  str_replace_all(":", " × ")
xlsx::write.xlsx(
  x = anova.model %>% round(3) %>%
    mutate(across(where(is.numeric), ~ format(.x, decimal.mark = "."))),
  sheetName = "p1A_anova",
  file = file.path(
    pathlist$result_path,
    paste0("lmer_results_", power.type, ".xlsx")
  ), append = TRUE
)

cs <- emtrends(model, pairwise ~ mov, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends # the slope of participants’ estimation error against beta power difference for each


cs <- emtrends(model, pairwise ~ task * gain, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends # the slope of participants’ estimation error against beta power difference for each

cs <- emtrends(model, pairwise ~ task * mov * gain, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends
```



**Additional investigation**: In the condition $\text{Judge Movement}:\text{Passive}:\text{Move > Touch}$, is the predicted estimation error ($\text{estError}$) equal to zero when the neural predictor ($\text{PowerDiff}$) is exactly zero?

- The Statistical Test: Contrasting the Estimated Marginal Mean (EMM) against Zero

- The $\text{emmeans}$ function can calculate the predicted mean of the dependent variable ($\text{estError}$) for any specific combination of factors, holding continuous predictors (like $\text{PowerDiff}$) at a specific value (e.g., zero).


```{r Against 0, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Step 1: Calculate the EMM at $\text{PowerDiff} = 0$
# 1. Define the specific condition of interest
condition_of_interest <- c(task = "Judge Movement", mov = "Passive", gain = "Move > Touch")

# 2. Use emmeans to find the predicted estError when PowerDiff is 0
emm_at_zero <- emmeans(model,
  specs = ~ task * mov * gain,
  at = list(PowerDiff = 0)
)
summary(emm_at_zero)

# 3. Filter the result to just your condition
emm_specific <- summary(emm_at_zero) %>%
  filter(task == "Judge Movement", mov == "Passive", gain == "Move > Touch")

# Step 2: Test the Hypothesis ($\text{Estimate} = 0$)
# Test the specific estimate against zero
test_result <- contrast(emm_at_zero,
  method = "revpairwise",
  by = "task", adjust = "none"
) # Use adjust="none" or "Tukey" as needed

# Filter the contrast output for the test: "Estimate vs. 0"
# (Note: Often, if the CI from Step 1 does not include zero, the test is redundant)
```

The most important finding here is which conditions are not biased when the neural predictor is neutral. This demonstrates where the behavioral effects of $\text{task}$, $\text{mov}$, and $\text{gain}$ effectively cancel each other out:

- Four conditions show NO significant bias at symmetrical processing ($\text{PowerDiff}=0$). This is quite powerful, as it suggests the behavioral effects of the sensory context are not a sufficient explanation for bias in these cases; the bias must be driven by the neural modulation ($\text{PowerDiff}$ interaction).

- Four conditions do show a significant bias, meaning the combined effects of $\text{task}$, $\text{mov}$, and $\text{gain}$ create an inherent bias that the neural state must counteract or enhance.



### Model 1B: New coding scheme

We assume that judging touch and judging movement are equivalent tasks, as well as no effect of modality on gain. Therefore, we apply for a mixed coding approach that kept the dummy coding of movement type (i.e., Passive condition as reference level) and sum-coded task (Judge Touch vs Judge Movement) and gain. 

```{r Model 1B, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
filter.timing <- "Full"
predictData <- parData %>%
  filter(flipped.gain != "1.Unity" & unimodal == "Self-touch" & timing == paste(filter.timing, "Movement")) %>%
  mutate(sbjN = factor(sbjN)) %>%
  mutate(
    estError = (resp - Target_length) / Target_length,
    GAIN = flipped.gain
  )


# CODING APPROACH 1: MIXED CODING APPROACH
# 1. Set Passive as the Reference (Dummy Coding)
# Assuming "Passive" is the first level alphabetically; if not, use relevel()
predictData$mov <- relevel(predictData$mov, ref = "Passive")
(contrasts(predictData$mov) <- contr.treatment(2))

# 2. Set Touch vs Move as Sum Coding (Effect Coding)
(contrasts(predictData$task) <- contr.sum(2))

# 3. Set Gain as Sum Coding (Effect Coding)
predictData$gain <- factor(predictData$gain, levels = c("Move < Touch", "Move > Touch"))
(contrasts(predictData$gain) <- contr.sum(2))

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov * gain + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
summary_df <- as.data.frame(summary(model)$coefficients) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  rownames_to_column("factor") %>%
  mutate(factor = factor %>%
    str_replace_all("PowerDiff", predictor.name) %>%
    str_replace_all("task1", "Task [JudgeTouch]") %>%
    str_replace_all("task2", "Task [JudgeMove]") %>%
    str_replace_all("mov1", "Movement [Passive]") %>%
    str_replace_all("mov2", "Movement [Active]") %>%
    str_replace_all("gain1", "Gain [M<T]") %>%
    str_replace_all("gain2", "Gain [M>T]") %>%
    str_replace_all(":", " × "))

xlsx::write.xlsx(
  x = summary_df %>%
    mutate(across(where(is.numeric), ~ format(.x, decimal.mark = "."))),
  sheetName = "p1B_lmer",
  file = file.path(
    pathlist$result_path,
    paste0("lmer_results_", power.type, ".xlsx")
  ), append = TRUE
)

# Generate predictions for PowerDiff across task, mov, and gain
pred <- ggpredict(model, terms = c("PowerDiff [all]", "task", "mov", "gain"))

x_axis <- ifelse(power.type == "raw",
  expression(paste("Beta Power Difference", " power (", mV^2, ")")),
  ifelse(power.type == "log",
    expression(paste("Beta Power Log-Ratio (dB)"))
  )
)
# Plot predictions
p0 <- ggplot(pred, aes(x = x, y = predicted, color = group)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  annotate("text", x = -.5, y = +Inf, label = sprintf("\u2190\u2190\u2190\nmotor-focused"), color = palette$two.color1[2], hjust = 1, vjust = "top", size = 12 / .pt) +
  annotate("text", x = +.5, y = +Inf, label = sprintf("\u2192\u2192\u2192\ntactile-focused"), color = palette$two.color1[1], hjust = 0, vjust = "top", size = 12 / .pt) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2) +
  facet_grid(panel ~ facet) + # Adjust based on ggpredict output (mov × gain)
  labs(
    title = paste("Predicting Judgement Error with Beta Power during", filter.timing, "Self-touch"),
    subtitle = paste0("Beta", predictor.name," x Task x Movement type x Gain"),
    x = x_axis,
    y = "Judgement Error\n(-1 = underestimation, 0 = accurate, +1 =overestimation)\n"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_fill_manual("Task", values = palette$two.color1) +
  theme(
    aspect.ratio = 1,
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
p0

(anova.model <- anova(model))
rownames(anova.model) <- rownames(anova.model) %>%
  str_replace_all("PowerDiff", predictor.name) %>%
  str_replace_all("task", "Task") %>%
  str_replace_all("mov", "Movement") %>%
  str_replace_all("gain", "Gain") %>%
  str_replace_all(":", " × ")
xlsx::write.xlsx(
  x = anova.model %>% round(3) %>%
    mutate(across(where(is.numeric), ~ format(.x, decimal.mark = "."))),
  sheetName = "p1B_anova",
  file = file.path(
    pathlist$result_path,
    paste0("lmer_results_", power.type, ".xlsx")
  ), append = TRUE
)


cs <- emtrends(model, pairwise ~ mov, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends # the slope of participants’ estimation error against beta power difference for each


cs <- emtrends(model, pairwise ~ task * gain, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends # the slope of participants’ estimation error against beta power difference for each

cs <- emtrends(model, pairwise ~ task * mov * gain, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends
```
