---
title: "TOUCH-BRAIN: Pre-Registration Plan"
author: "Phuc TU Nguyen"
date: "2025-06-06"

output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    toc: true
    toc_depth: 3
    number_sections: true
    collapse: true
---

```{r setup, warning=FALSE, echo=FALSE, message=FALSE}
## Set up libraries and define paths with function

rm(list = ls())
library(rstudioapi)

script_path <- dirname(rstudioapi::getActiveDocumentContext()$path)
function_path <- file.path(script_path, "function")

source(file.path(function_path, "loadconfig.R"))
load_lib()
load_path(script_path)
load_palette()

phases <- c(
  "Movement Cue",
  "Before Movement",
  "During Movement",
  "Early Movement", "Half Movement", "Late Movement", "Full Movement",
  "After Movement"
)
vps <- c("P")
```


# Pool and preprocess data

Behavioral and EEG data are merged across all participants and blocks. Block number and trial number are assigned per condition (t/m &times; a/p &times; unimodal/both)

```{r Pool beh, warning=FALSE, message=FALSE, echo=FALSE}
source(file.path(function_path, "loaddata.R"))

beh_combined_df <- load_behdata(vps, pathlist$beh_data_path)
beh_combined_df <- adjust_beh_df(beh_combined_df)
# Test for sufficient blocks
beh_test <- beh_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial_beh = n(), .groups = "drop")
```

```{r Pool eeg, warning=FALSE, message=FALSE, echo=FALSE}
eeg_combined_df <- load_eegdata(vps, file.path(pathlist$eeg_data_path, "Revise_5Phase"))

# Adjustment according to protocol
{
  empty_row <- eeg_combined_df[1, ]
  empty_row[1, ] <- NA

  empty_row$filename <- "P23_move_active_results.xls"
  eeg_combined_df <- rbind(
    eeg_combined_df[1:(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[36]), ],
    empty_row,
    eeg_combined_df[(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[37]):nrow(eeg_combined_df), ]
  )
  eeg_combined_df <- eeg_combined_df[-which(eeg_combined_df$filename == "P23_move_passive_results.xlsx")[51], ]
}


eeg_combined_df <- adjust_eeg_df(eeg_combined_df)


# Test for sufficient blocks
eeg_test <- eeg_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial = n(), .groups = "drop")

# Compare trial counts between behavioral and EEG data
testmerge <- left_join(beh_test, eeg_test,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal")
) %>%
  arrange(NAME, unimodal, QUESTION, ACTIVE) %>%
  mutate(trialdiff = ntrial_beh - ntrial)
```

```{r Merge beh and eeg data, warning=FALSE, message=FALSE, echo=FALSE}
# Merge full behavioral and EEG datasets
merge_df <- left_join(beh_combined_df, eeg_combined_df,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal", "trial_number")
)

# Compare trial counts between behavioral and EEG data
testmerge1 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())
```

```{r Remove data, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# Remove specific blocks for specific subjects
merge_df <- merge_df %>%
  filter(!(NAME == "P03" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "p" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P17" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P22" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P23" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "p" & trial_number %in% c(50))) %>%
  filter(!(NAME == "P25" & !is.na(unimodal) & unimodal == "1" & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(1))) %>%
  # temporary filter due to unsatisfactory preprocessing
  filter(!(NAME %in% c("P11", "P17", "P22")))

testmerge2 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

testmerge3 <- merge_df %>%
  mutate(
    NAME = str_extract(NAME, "\\d+") %>% as.numeric(),
    unimodal = case_when(
      unimodal %in% c("1", "2") ~ "Unimodal",
      !unimodal %in% c("1", "2") ~ "Self_touch"
    )
  ) %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

ggplot(testmerge3) +
  geom_point(aes(x = NAME, y = n, color = unimodal)) +
  facet_wrap(QUESTION ~ ACTIVE) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  labs(
    title = "Check for data completeness - Before Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )


demogr_df <- read_xlsx(file.path(pathlist$demogr_data_path, "demographic.xlsx"))
merge_df <- left_join(merge_df, demogr_df, by = "NAME")

test <- merge_df %>% filter(is.na(unimodal))
```

```{r Save merged data, warning=FALSE, message=FALSE, echo=FALSE}
# Export merged data to Excel
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
write_xlsx(merge_df, file.path(pathlist$result_path, xlsx_name))
# print(codebookr::codebook(rawData), file.path(pathlist$result_path,"ST_EEG_Codebook.docx"))

rm(list = c(
  "demogr_df",
  "beh_combined_df", "beh_test",
  "eeg_combined_df", "eeg_test",
  "empty_row",
  "merge_df",
  ls(pattern = "^test")
))
```


```{r Read from csv, warning=FALSE, message=FALSE, echo=FALSE}
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
source(file.path(function_path, "preprocessdata.R"))
# channels <- expand.grid(c("F", "Fc", "FC", "C", "CP", "P"), c("3", "5", "z", "4", "6"))
channels <- expand.grid(c("C"), c("3", "4"))
channels <- paste0(channels$Var1, channels$Var2)
```

**Target Length**: based on the task type (touchLength or movLength is selected).

**Gain/Flipped Gain**: 1 = Unity (move=touch), 2 = NonUnity, incl move>touch and move<touch.

**Condition Labels (condN)**: (1) Self-touch Active - Judge Touch, 
(2) Self-touch Passive - Judge Touch, 
(3) Self-touch Active - Judge Move, 
(4) Self-touch Passive - Judge Move*, 
(5) Unimodal - Judge Touch, 
(6) Unimodal Active - Judge Move, 
(7) Unimodal Passive - Judge Move. 

**Flipped Gain**: Calculated as $|\frac{TargetLength}{InterferenceLength}\ |$.        **Absolute Error**: Calculated as $|\frac{ReportedLength}{TargetLength}\ - 1|$.

```{r Preprocess data, layout="l-body-outset", fig.width=4, fig.height=4, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
options(width = 500)

rawData <- read_excel(path = file.path(pathlist$result_path, xlsx_name))
rawData <- preprocess_beh_df(rawData) %>%
  select(
    sbjN, Gender, trialN, task, mov, unimodal, condN, BLOCK, trial_number, DURATION, MovDur, HalfDur,
    gain, flipped.gain, touchLength, movLength, Target_length, Interference_length, resp, estError, absError, delta,
    starts_with(channels)
  )

rawData %>%
  select(
    sbjN, condN, BLOCK, trialN, flipped.gain, Target_length, resp,
    matches("^(C3|C4).*_(pre|full|early|late)$")
  ) %>%
  arrange(sbjN, condN, BLOCK, trialN) %>%
  rmarkdown::paged_table(options = list(rows.print = 5, cols.print = 9))
```


# Removing outliers

Extreme responses at both end (too large or too small estimation) are excluded because participants pressed arrows too quick and submitted responses immediately.


```{r Filter extreme responses, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# Make long data
rawData.filter <- filter_outliers(
  df = rawData %>% mutate(puffer = 1 %>% as.factor()),
  value_col = "resp", group_cols = c("puffer")
) # filter extreme response
ggplot(rawData) +
  geom_histogram(aes(x = resp)) +
  scale_x_continuous("Estimation Response (cm)", limits = c(0, 20), breaks = seq(0, 20, 10)) +
  labs(title = "Response distribution before filtering out outliers")
ggplot(rawData.filter) +
  geom_histogram(aes(x = resp)) +
  scale_x_continuous("Estimation Response (cm)", limits = c(0, 20), breaks = seq(0, 20, 10)) +
  labs(title = "Response distribution after filtering out outliers")

ggplot(rawData.filter) +
  geom_histogram(aes(x = MovDur)) +
  scale_x_continuous("Move Duration (s)", limits = c(0, 10), breaks = seq(0, 20, 10)) +
  labs(title = "Distribution of Moving Duration (excluded: more than 8s)")
```

Extreme Beta power values at both end (too large or too small) are filtered out at both end. 

**Idea: (1) Think about filtering out only the extreme large values. (2) Log transform for skewed data**

```{r Filter extreme beta power values, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
longrawData <- long_beh_eeg_df(rawData.filter)
longData <- filter_outliers(df = longrawData, value_col = "powerBeta", group_cols = c("channellocation_timing")) # filter extreme Beta power values

ggplot(longrawData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5) +
  facet_wrap(~timing) +
  labs(title = "Distribution of Beta Power before filtering out outliers")

ggplot(longData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5) +
  facet_wrap(~timing) +
  labs(title = "Distribution of Beta Power after filtering out outliers")

shortData <- short_beh_eeg_df(longData %>% select(sbjN:powerBeta)) %>%
  mutate(unimodal = as.factor(unimodal))

testmerge4 <- shortData %>%
  mutate(sbjN = str_extract(sbjN, "\\d+") %>% as.numeric()) %>%
  group_by(sbjN, task, mov, unimodal) %>%
  summarise(n = n()) %>%
  mutate(remain_percent = case_when(
    unimodal == "Self-touch" ~ n / 54,
    unimodal == "Unimodal" ~ n / 36
  ))

ggplot(testmerge4) +
  geom_point(aes(x = sbjN, y = n, color = unimodal)) +
  facet_wrap(task ~ mov) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  labs(
    title = "Check for data completeness - After Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )

# To calculate change of Beta power
# present data frame_ one column for C3, one column for C4
parData <- longData %>%
  select(sbjN:delta, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

byBaseline.shortData <- shortData %>%
  select(sbjN:absError, starts_with("C3"), starts_with("C4")) %>%
  rowwise() %>%
  mutate(
    C3_full = 100 * (C3_full - C3_pre) / C3_pre,
    C4_full = 100 * (C4_full - C4_pre) / C4_pre,
    C3_early = 100 * (C3_early - C3_pre) / C3_pre,
    C4_early = 100 * (C4_early - C4_pre) / C4_pre,
    C3_late = 100 * (C3_late - C3_pre) / C3_pre,
    C4_late = 100 * (C4_late - C4_pre) / C4_pre
  ) %>%
  mutate(C3_pre = 0, C4_pre = 0)


byBaseline.longData <- long_beh_eeg_df(byBaseline.shortData)

# Create a unique trial ID in both datasets
longData <- longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

byBaseline.longData <- byBaseline.longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

# Filter byBaseline.longData to keep only rows present in longData - remove outliers based off the raw power Beta
byBaseline.longData <- byBaseline.longData %>%
  filter(trialID %in% longData$trialID)


byBaseline.parData <- byBaseline.longData %>%
  select(sbjN:absError, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

rm(list = c(ls(pattern = "raw|test")))
```


# Participants
```{r Demographics, fig.width=16, fig.height=10, echo=FALSE, warning=FALSE, message=FALSE} 
# Sex distribution
shortData %>%
  distinct(sbjN, Gender) %>%
  group_by(Gender) %>%
  summarise(n = n()) %>%
  mutate(per = n / sum(n)) %>%
  ggplot() +
  geom_col(aes(x = Gender, y = 100 * per, fill = Gender), show.legend = F) +
  labs(
    title = "Participant - Sex",
    x = "Sex", y = "Percentage (%)"
  ) +
  theme(aspect.ratio = 1)
```


# Behavioral results

```{r Behavioral Plots, fig.width=16, fig.height=10, echo=FALSE, warning=FALSE, message=FALSE} 
# Subject-level aggregation
plotData <- shortData %>%
  group_by(sbjN, task, mov, unimodal, gain, Target_length) %>%
  summarise(response = mean(resp), .groups = "drop") %>%
  group_by(task, mov, unimodal, gain, Target_length) %>%
  summarise(
    mean = mean(response),
    se = sd(response) / sqrt(n()), # SE across subjects
    n = n(),
    .groups = "drop"
  )

# Plot
p1 <- ggplot(data = plotData %>% filter(unimodal == "Self-touch")) +
  geom_point(aes(x = Target_length, y = mean, color = gain), show.legend = F) +
  geom_line(aes(x = Target_length, y = mean, color = gain, group = gain), show.legend = F) +
  geom_ribbon(aes(
    x = Target_length, ymin = mean - se, ymax = mean + se,
    fill = gain, group = gain
  ), alpha = 0.15, show.legend = F) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(task ~ mov) +
  scale_x_continuous(limits = c(2, 10), breaks = seq(4, 8, by = 2)) +
  scale_y_continuous(limits = c(2, 10), breaks = seq(2, 10, by = 2)) +
  labs(
    title = "Self-touch Conditions",
    x = "Actual target extent (cm)", y = "",
    color = "Gain", fill = "Gain"
  ) +
  theme(
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )

p2 <- ggplot(data = plotData %>% filter(unimodal == "Unimodal")) +
  geom_point(aes(x = Target_length, y = mean, color = gain), show.legend = T) +
  geom_line(aes(x = Target_length, y = mean, color = gain, group = gain), show.legend = T) +
  geom_ribbon(aes(
    x = Target_length, ymin = mean - se, ymax = mean + se,
    fill = gain, group = gain
  ), alpha = 0.15, show.legend = T) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(task ~ mov, drop = T) +
  scale_x_continuous(limits = c(2, 10), breaks = seq(4, 8, by = 2)) +
  scale_y_continuous(limits = c(2, 10), breaks = seq(2, 10, by = 2)) +
  labs(
    title = "Unimodal Conditions",
    x = "Actual target extent (cm)", y = "Perceived target extent (cm)",
    color = "Gain", fill = "Gain"
  ) +
  theme(
    legend.position = c(.15, .9),
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.key = element_blank(),
    legend.background = element_rect(fill = "transparent"),
    legend.title = element_text(size = 16)
  )

grid.arrange(p2, p1, ncol = 2)
```

## Calculate Interference Coefficients
```{r ICs, fig.height= 4, fig.width= 7}
w <- shortData %>%
  filter(unimodal == "Self-touch") %>%
  # filter(gain != 1.25, gain != 0.8)  %>%
  group_by(sbjN, mov, task) %>%
  do({
    model <- lm(resp ~ 0 + touchLength + movLength, data = .)
    as.data.frame(t(coef(model)))
  }) %>%
  ungroup() %>%
  mutate(
    normTouch = touchLength / (movLength + touchLength),
    normMove = movLength / (movLength + touchLength),
    weights = case_when(
      task == "Judge Touch" ~ normMove,
      task == "Judge Movement" ~ normTouch
    )
  )

w$mov <- factor(w$mov, levels = c("Active", "Passive"))

wideW <- w %>%
  select(-c(touchLength, movLength, normTouch, normMove)) %>%
  pivot_wider(
    names_from = c(task, mov), # Columns to use for names
    values_from = c(weights), # Values to fill in the table
    names_sep = "_"
  )
# clipr::write_clip(wideW)

ggplot(w, aes(x = mov, y = weights, fill = interaction(mov, task))) +
  geom_bar(stat = "summary", show.legend = FALSE) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  facet_wrap(~task) +
  ylim(0, 1) +
  labs(
    x = "Condition",
    y = "Weigt of task-irrelevant information (ω)",
    title = "Mean Interference Weights (ω) Across Movement and Judgment Conditions"
  ) +
  theme(
    aspect.ratio = 2,
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )
```

## Run ANOVA
```{r Behavioral ANOVA,}
full_ANOVA <- aov_ez(
  id = "sbjN",
  dv = "weights",
  within = c("mov", "task"),
  data = w,
  anova_table = list(correction = "GG", es = "pes") # request partial eta squared
)

# Use nice() to display the ANOVA table with effect sizes:
nice(full_ANOVA)
```

# Research questions
## Variables

  - **Judgement Error** quantifies *perceptual interference* with both positive and negative value, i.e., overestimation and negative estimation, respectively.
  
  $$Judgement Error = \frac{reported length}{true length}\ - 1$$
  
  - **ABSOLUTE Judgement Error** quantifies *perceptual interference* without negative value, i.e., the degree to which the perceptual judgement deviates from the true value OR how much the perceptual judgement is interfered by other information.
  
  $$ABSOLUTE Judgement Error = |JudgementError| = |\frac{reported length}{true length}\ - 1|$$
  
  - **Beta Power Difference** between the left hemisphere (C3) and the right hemisphere (C4) represents the degree to which motor activity interferes with tactile processing. Positive difference implies weaker interference of motor information (tactile focus), while negative difference implies stronger interference of motor information (motor focus).
  
  $$\Delta{B} = B_{C3} - B_{C4}$$
  

Because movement and tactile spatial percepts during self-touch are interfered by the processing of tactile and movement information, respectively, we expect that the neural marker of these two components could be used to predict judgement accuracy. For example, a negative difference in beta power between C3 and C4 *(C3 - C4)* reflects larger processing of motor information relative to tactile information and may suggest that motor information is weighted more in length judgement than tactile judgement

<p style="text-align: justify;">

## ERD

Check for ERD/S

```{r ERD Plots, fig.width=16, fig.height=10, echo=FALSE, warning=FALSE, message=FALSE} 
plotData <- longData %>%
  filter(unimodal == "Unimodal" & timing != "Full Movement") %>%
  group_by(condN, timing, relativehemisphere, location) %>%
  get_summary_stats(powerBeta)
# summarise(powerBeta=mean(powerBeta))

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN), size = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), size = 1) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), size = 2) +
  facet_wrap(~relativehemisphere) +
  scale_color_manual("Condition", values = palette$three.color2) +
  labs(
    title = "Beta Power in unimodal conditions at contra-lateral hemisphere",
    x = "Movement Phases",
    # y = expression(paste("x axis ", ring(A)^2)),
    y = expression(paste("Averaged ", Beta, " power (", mV^2, ")"))
  ) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )


plotData <- byBaseline.longData %>%
  filter(unimodal == "Unimodal" & timing != "Full Movement") %>%
  group_by(condN, timing, relativehemisphere, location) %>%
  get_summary_stats(powerBeta)

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN), size = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), size = 1) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), size = 2) +
  facet_wrap(~relativehemisphere) +
  scale_color_manual("Condition", values = palette$three.color2) +
  labs(
    title = "Beta ERD in unimodal conditions at contra-lateral hemisphere",
    x = "Movement Phases",
    y = "Percentage change (%)"
  ) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )
```




## Self-touch: Interhemispheric interference
**Does the relative difference in beta power between channel C3 and C4 during self-touch explain the asymmetrical, bidirectional interference of movement and tactile spatial percepts?**

H: Negative difference in the beta power between the channels C3 and C4 [C3-C4] (i.e., stronger motor processing than tactile processing) is associated with smaller error in move judgement and smaller tactile judgement.

### Model 0: Does interhemispheric balance predict How accurate participants are around the target?

```{r Model 0, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
filter.timing <- "Full"
predictData <- parData %>%
  filter(flipped.gain != "1.Unity" & unimodal == "Self-touch" & timing == paste(filter.timing, "Movement")) %>%
  mutate(sbjN = factor(sbjN)) %>%
  mutate(
    estError = (resp - Target_length) / Target_length,
    GAIN = flipped.gain
  )

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov * gain + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
summary_df <- as.data.frame(summary(model)$coefficients) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  rownames_to_column("factor")
xlsx::write.xlsx(x = summary_df %>% 
                   mutate(across(where(is.numeric), ~ format(.x, decimal.mark = "."))), 
                 sheetName = "p0_lmer", file = file.path(pathlist$result_path, "lmer_results.xlsx"), append = TRUE)

# Generate predictions for PowerDiff across task, mov, and gain
pred <- ggpredict(model, terms = c("PowerDiff [all]", "task", "mov", "gain"))

# Plot predictions
p0 <- ggplot(pred, aes(x = x, y = predicted, color = group)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  annotate("text", x = -.5, y = +Inf, label = sprintf("\u2190\u2190\u2190\nmotor-focused"), color = palette$two.color1[2], hjust = 1, vjust = "top", size = 12 / .pt) +
  annotate("text", x = +.5, y = +Inf, label = sprintf("\u2192\u2192\u2192\ntactile-focused"), color = palette$two.color1[1], hjust = 0, vjust = "top", size = 12 / .pt) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2) +
  facet_grid(panel ~ facet) + # Adjust based on ggpredict output (mov × gain)
  labs(
    title = paste("Predicting Judgement Error with Beta Power during",filter.timing,"Self-touch"),
    subtitle = "PowerDiff * Task * Movement type * Gain",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(-1 = underestimation, 0 = accurate, +1 =overestimation)\n"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_fill_manual("Task", values = palette$two.color1) +
  theme(
    aspect.ratio = 1,
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
p0

anova(model)
xlsx::write.xlsx(
  x = anova(model) %>% round(3) %>%
    mutate(across(where(is.numeric), ~ format(.x, decimal.mark = "."))),
  sheetName = "p0_anova",
  file = file.path(pathlist$result_path, "lmer_results.xlsx"), append = TRUE
)
cs <- emtrends(model,  pairwise ~ mov, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends


cs <- emtrends(model, pairwise ~ task * gain, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends

cs <- emtrends(model, pairwise ~ task * mov* gain, var = "PowerDiff")
css <- summary(cs)
css$contrasts
css$emtrends

```

