---
title: "TOUCH-BRAIN: Pre-Registration Plan"
author: "Phuc TU Nguyen"
date: "2025-06-06"

output:
  html_document:
    theme: flatly       
    highlight: tango     # Nice syntax highlighting for R code
    toc: true
    toc_depth: 4
    toc_float: 
      collapsed: false   # Keeps the TOC expanded
      smooth_scroll: true
    number_sections: true
    code_folding: hide   
    df_print: paged      # Makes large data frames look like neat tables
---

```{r setup, warning=FALSE, echo=FALSE, message=FALSE}
## Set up libraries and define paths with function

rm(list = ls())
library(rstudioapi)

script_path <- dirname(rstudioapi::getActiveDocumentContext()$path)
function_path <- file.path(script_path, "function")

source(file.path(function_path, "loadconfig.R"))
load_lib()
load_path(script_path)
load_palette()

script_time <- format(Sys.time(), ("%d%m%Y_%H%M"))

phases <- c(
  "Movement Cue",
  "Before Movement",
  "During Movement",
  "Early Movement", "Half Movement", "Late Movement", "Full Movement",
  "After Movement"
)
vps <- c("P")
power.type <- c("raw", "log")[1] # change the format of Beta power here
predictor.name <- ifelse(power.type == "log", "Power Log-Ratio", "Power Difference")
```


# Pool and preprocess data

Behavioral and EEG data are merged across all participants and blocks. Block number and trial number are assigned per condition (t/m &times; a/p &times; unimodal/self-touch)

```{r Pool beh, warning=FALSE, message=FALSE, echo=FALSE}
source(file.path(function_path, "loaddata.R"))

beh_combined_df <- load_behdata(vps, pathlist$beh_data_path)
beh_combined_df <- adjust_beh_df(beh_combined_df)
# Test for sufficient blocks
beh_test <- beh_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial_beh = n(), .groups = "drop")
```

```{r Pool eeg, warning=FALSE, message=FALSE, echo=FALSE}
eeg_combined_df <- load_eegdata(vps, file.path(pathlist$eeg_data_path, "Revise_5Phase"))

# Adjustment according to protocol
{
  empty_row <- eeg_combined_df[1, ]
  empty_row[1, ] <- NA

  empty_row$filename <- "P23_move_active_results.xls"
  eeg_combined_df <- rbind(
    eeg_combined_df[1:(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[36]), ],
    empty_row,
    eeg_combined_df[(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[37]):nrow(eeg_combined_df), ]
  )
  eeg_combined_df <- eeg_combined_df[-which(eeg_combined_df$filename == "P23_move_passive_results.xlsx")[51], ]
}


eeg_combined_df <- adjust_eeg_df(eeg_combined_df)


# Test for sufficient blocks
eeg_test <- eeg_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial = n(), .groups = "drop")

# Compare trial counts between behavioral and EEG data
testmerge <- left_join(beh_test, eeg_test,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal")
) %>%
  arrange(NAME, unimodal, QUESTION, ACTIVE) %>%
  mutate(trialdiff = ntrial_beh - ntrial)
```

```{r Merge beh and eeg data, warning=FALSE, message=FALSE, echo=FALSE}
# Merge full behavioral and EEG datasets
merge_df <- left_join(beh_combined_df, eeg_combined_df,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal", "trial_number")
)

# Compare trial counts between behavioral and EEG data
testmerge1 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())
```

```{r Remove data, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# Remove specific blocks for specific subjects
merge_df <- merge_df %>%
  filter(!(NAME == "P03" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "p" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P17" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P22" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P23" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "p" & trial_number %in% c(50))) %>%
  filter(!(NAME == "P25" & !is.na(unimodal) & unimodal == "1" & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(1))) %>%
  # temporary filter due to unsatisfactory preprocessing
  filter(!(NAME %in% c("P11", "P17", "P22")))

testmerge2 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

testmerge3 <- merge_df %>%
  mutate(
    NAME = str_extract(NAME, "\\d+") %>% as.numeric(),
    unimodal = case_when(
      unimodal %in% c("1", "2") ~ "Unimodal",
      !unimodal %in% c("1", "2") ~ "Self-touch"
    ),
    QUESTION = case_when(
      QUESTION == "t" ~ "Judge Touch",
      QUESTION == "m" ~ "Judge Move"
    ) %>% factor(levels = c("Judge Touch", "Judge Move")),
    ACTIVE = case_when(
      ACTIVE == "a" ~ "Active",
      ACTIVE == "p" ~ "Passive"
    ) %>% factor(levels = c("Passive", "Active"))
  ) %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

ggplot(testmerge3) +
  geom_point(aes(x = NAME, y = n, color = unimodal)) +
  facet_wrap(QUESTION ~ ACTIVE) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  scale_color_discrete("Condition") +
  labs(
    title = "Check for data completeness - Before Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )


demogr_df <- read_xlsx(file.path(pathlist$demogr_data_path, "demographic.xlsx"))
merge_df <- left_join(merge_df, demogr_df, by = "NAME")

test <- merge_df %>% filter(is.na(unimodal))
```

```{r Save merged data, warning=FALSE, message=FALSE, echo=FALSE}
# Export merged data to Excel
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
write_xlsx(merge_df, file.path(pathlist$result_path, xlsx_name))
# print(codebookr::codebook(rawData), file.path(pathlist$result_path,"ST_EEG_Codebook.docx"))

rm(list = c(
  "demogr_df",
  "beh_combined_df", "beh_test",
  "eeg_combined_df", "eeg_test",
  "empty_row",
  "merge_df",
  ls(pattern = "^test")
))
```


```{r Read from csv, warning=FALSE, message=FALSE, echo=FALSE}
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
source(file.path(function_path, "preprocessdata.R"))
# channels <- expand.grid(c("F", "Fc", "FC", "C", "CP", "P"), c("3", "5", "z", "4", "6"))
channels <- expand.grid(c("C"), c("3", "4"))
channels <- paste0(channels$Var1, channels$Var2)
```

**Target Length**: based on the task type (touchLength or movLength is selected).

**Gain/Flipped Gain**: 1 = Unity (move=touch), 2 = NonUnity, incl Move > Touch and Move < Touch.

**Condition Labels (condN)**: (1) Self-touch Active - Judge Touch, 
(2) Self-touch Passive - Judge Touch, 
(3) Self-touch Active - Judge Move, 
(4) Self-touch Passive - Judge Move*, 
(5) Unimodal - Judge Touch, 
(6) Unimodal Active - Judge Move, 
(7) Unimodal Passive - Judge Move. 

**Flipped Gain**: Calculated as $|\frac{TargetLength}{InterferenceLength}\ |$.        **Absolute Error**: Calculated as $|\frac{ReportedLength}{TargetLength}\ - 1|$.

```{r Preprocess data, layout="l-body-outset", fig.width=4, fig.height=4, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
options(width = 500)

rawData <- read_excel(path = file.path(pathlist$result_path, xlsx_name))
rawData <- preprocess_beh_df(rawData) %>%
  select(
    sbjN, Gender, trialN, task, mov, unimodal, condN, BLOCK, trial_number, DURATION, MovDur, HalfDur,
    gain, flipped.gain, touchLength, movLength, Target_length, Interference_length, resp, estError, absError, delta,
    # ExclCode,
    starts_with(channels)
  )

rawData %>%
  select(
    sbjN, condN, BLOCK, trialN, flipped.gain, Target_length, Interference_length, resp,
    matches("^(C3|C4).*_(pre|full|early|late)$")
  ) %>%
  arrange(sbjN, condN, BLOCK, trialN) %>%
  rmarkdown::paged_table(options = list(rows.print = 5, cols.print = 10))
```


# Removing outliers

Idea: Extreme slow or quick movement could be excluded because participants pressed arrows too quick and submitted responses immediately.

## Beh: Movement duration

```{r Filter abnormal movement, fig.width=12, fig.height=5, echo=TRUE, warning=FALSE, message=FALSE}
# Calculate IQR boundaries for MovDur
q1 <- quantile(rawData$MovDur, 0.25, na.rm = TRUE)
q3 <- quantile(rawData$MovDur, 0.75, na.rm = TRUE)
iqr_val <- q3 - q1
upper_iqr_limit <- q3 + (1.5 * iqr_val)
lower_iqr_limit <- q1 - (1.5 * iqr_val)

# Create a summary table
exclusion_check <- rawData %>%
  summarise(
    Total_Trials = n(),
    Missing_Dur = sum(is.na(MovDur)), # due to EEG analyses: epoch rejection or movement longer than 8s
    Outliers_IQR_High = sum(MovDur > upper_iqr_limit, na.rm = TRUE), # movement too slow
    Outliers_IQR_Low = sum(MovDur < lower_iqr_limit, na.rm = TRUE) # movement to quick
  )

# Print summary
cat(sprintf(
  "%d/%d trials removed: %.2f%%\n",
  exclusion_check$Missing_Dur,
  exclusion_check$Total_Trials,
  100 * (exclusion_check$Missing_Dur) / exclusion_check$Total_Trials
))

# Which participants have missing MovDur
(rawData %>%
  filter(is.na(MovDur)) %>%
  count(sbjN, condN))

rawData <- rawData %>%
  filter(!is.na(MovDur))

p1 <- ggplot(rawData) +
  geom_histogram(aes(x = MovDur)) +
  scale_x_continuous("Move Duration (s)", limits = c(0, 10), breaks = seq(0, 20, 10)) +
  labs(title = "Distribution of Moving Duration (excluded: more than 6.8 s)")
summary(rawData$MovDur)
p1
```


## Beh: Extreme Responses

Extreme responses at both end (too large or too small estimation) are excluded because participants pressed arrows too quick and submitted responses immediately.


```{r Filter extreme responses, fig.width=12, fig.height=5, echo=TRUE, warning=FALSE, message=FALSE}
# Make long data
filter.choice <- list(
  "puffer", # extreme responses across all participants
  "sbjN" # extreme responses of each participant
)

rawData.filter <- filter_outliers(
  df = rawData %>% mutate(puffer = 1 %>% as.factor()),
  value_col = "estError", group_cols = filter.choice[[1]]
) # filter extreme response
ggplot(rawData) +
  geom_histogram(aes(x = 100 * estError)) +
  scale_x_continuous("Estimation Error (%)", limits = c(-150, 300)) +
  labs(title = "Response distribution before filtering out outliers")
ggplot(rawData.filter) +
  geom_histogram(aes(x = 100 * estError)) +
  scale_x_continuous("Estimation Error (%)", limits = c(-150, 300)) +
  labs(title = "Response distribution after filtering out outliers")

# --- Calculate Data Loss ---
# Print summary
cat(sprintf(
  "%d/%d trials removed: %.2f%%\n",
  nrow(rawData) - nrow(rawData.filter),
  nrow(rawData),
  100 * (nrow(rawData) - nrow(rawData.filter)) / nrow(rawData)
))

# Identify which conditions are losing the most data
(loss_report <- rawData %>%
  anti_join(rawData.filter, by = c("sbjN", "condN", "BLOCK", "trial_number")) %>%
  count(condN, name = "excluded_count"))

```


## EEG: Extreme Beta power values

Extreme Beta power values at both end (too large or too small) are filtered out at both end. 

**Idea: (1) Filter out the extreme raw values. (2) Filter out the extreme raw values + Log transform for skewed data**. In this case, we went for the `r ifelse(power.type == "raw","first","second")` method.

```{r Filter extreme beta power values, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
filter.choice <- list(
  "puffer", # extreme responses across all participants
  "sbjN", # extreme responses of each participant
  c("sbjN", "channellocation_timing"), # filter extreme Beta power values by participant and electrode position and timing
  "channellocation_timing"
)
longrawData <- long_beh_eeg_df(rawData.filter)

# raw data require filtering outliers
longData <- filter_outliers(df = longrawData, value_col = "powerBeta", group_cols = filter.choice[[4]])
# # Or log-transform
# longData <- longrawData

ggplot(longrawData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5, position = "identity") +
  facet_wrap(~timing) +
  scale_x_continuous(expression(paste("Beta Power (", mV^2, ")"))) +
  # scale_y_continuous(limits = c(0, 2000)) +
  labs(title = "Distribution of Raw Beta Power before filtering out outliers")
ggplot(longData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5, position = "identity") +
  facet_wrap(~timing) +
  scale_x_continuous(expression(paste("Beta Power", " power (", mV^2, ")"))) +
  # scale_y_continuous(limits = c(0, 2000)) +
  labs(title = "Distribution of Raw Beta Power after filtering out outliers")

if (power.type == "log") {
  longData <- longData %>%
    mutate(across(starts_with(c("powerBeta")), ~ 10 * log10(.x))) # log-transformation

  ggplot(longData) +
    geom_histogram(aes(x = powerBeta, fill = location), alpha = .5, position = "identity") +
    facet_wrap(~timing) +
    scale_x_continuous(expression(paste("Beta Power (dB)"))) +
    # scale_y_continuous(limits = c(0, 2000)) +
    labs(title = "Distribution of Log-Transformed Beta Power after filtering out outliers")
}


shortData <- short_beh_eeg_df(longData %>% select(sbjN:powerBeta)) %>%
  mutate(unimodal = as.factor(unimodal))

# --- Calculate Data Loss ---
# Identify which conditions are losing the most data
(loss_report <- rawData.filter %>%
  anti_join(shortData, by = c("sbjN", "trial_number", "condN", "BLOCK")) %>%
  count(sbjN,condN, BLOCK,trial_number, name = "excluded_count"))

cat(sprintf(
  "%d/%d trials removed: %.2f%%\n",
  sum(loss_report$excluded_count),
  nrow(rawData.filter),
  100 * sum(loss_report$excluded_count) / nrow(rawData.filter)
))


# To calculate change of Beta power
# present data frame in one column for C3, one column for C4
parData <- longData %>%
  select(sbjN:delta, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

ggplot(parData) +
  geom_histogram(aes(x = PowerDiff), alpha = .5, position = "identity") +
  facet_wrap(~timing) +
  scale_x_continuous(sprintf("Beta %s C3-C4", predictor.name)) +
  # scale_y_continuous(limits = c(0, 2000)) +
  labs(title = sprintf("Distribution of Beta %s after filtering out outliers", predictor.name))

byBaseline.shortData <- shortData %>%
  select(sbjN:absError, starts_with("C3"), starts_with("C4"))


if (power.type == "raw") {
  byBaseline.shortData <- byBaseline.shortData %>%
    rowwise() %>%
    # For raw data:
    mutate(
      C3_full = 100 * (C3_full - C3_pre) / C3_pre,
      C4_full = 100 * (C4_full - C4_pre) / C4_pre,
      C3_early = 100 * (C3_early - C3_pre) / C3_pre,
      C4_early = 100 * (C4_early - C4_pre) / C4_pre,
      C3_late = 100 * (C3_late - C3_pre) / C3_pre,
      C4_late = 100 * (C4_late - C4_pre) / C4_pre
    ) %>%
    mutate(C3_pre = 0, C4_pre = 0)
}

if (power.type == "log") {
  byBaseline.shortData <- byBaseline.shortData %>%
    rowwise() %>%
    # For Decibels (Log) data
    mutate(
      C3_full = (C3_full - C3_pre),
      C4_full = (C4_full - C4_pre),
      C3_early = (C3_early - C3_pre),
      C4_early = (C4_early - C4_pre),
      C3_late = (C3_late - C3_pre),
      C4_late = (C4_late - C4_pre)
    ) %>%
    mutate(C3_pre = 0, C4_pre = 0)
}

byBaseline.longData <- long_beh_eeg_df(byBaseline.shortData)

# Create a unique trial ID in both datasets
longData <- longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

byBaseline.longData <- byBaseline.longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

# Filter byBaseline.longData to keep only rows present in longData - remove outliers based off the raw power Beta
byBaseline.longData <- byBaseline.longData %>%
  filter(trialID %in% longData$trialID)


byBaseline.parData <- byBaseline.longData %>%
  select(sbjN:absError, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

testmerge4 <- shortData %>%
  mutate(sbjN = str_extract(sbjN, "\\d+") %>% as.numeric()) %>%
  group_by(sbjN, task, mov, unimodal) %>%
  summarise(n = n()) %>%
  mutate(remain_percent = case_when(
    unimodal == "Self-touch" ~ n / 54,
    unimodal == "Unimodal" ~ n / 36
  ))

ggplot(testmerge4) +
  geom_point(aes(x = sbjN, y = n, color = unimodal)) +
  facet_wrap(task ~ mov) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  scale_color_discrete("Condition") +
  labs(
    title = "Check for data completeness - After Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )

rm(list = c(ls(pattern = "raw|test")))
```


# Participants
```{r Demographics, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Sex distribution
shortData %>%
  distinct(sbjN, Gender) %>%
  group_by(Gender) %>%
  summarise(n = n()) %>%
  mutate(per = n / sum(n)) %>%
  ggplot() +
  geom_col(aes(x = Gender, y = 100 * per, fill = Gender), show.legend = F) +
  labs(
    title = "Participant - Sex",
    x = "Sex", y = "Percentage (%)"
  ) +
  theme(
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )
```


# Behavioral results

```{r Behavioral Plots, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Subject-level aggregation
plotData <- shortData %>%
  group_by(sbjN, task, mov, unimodal, gain, Target_length) %>%
  summarise(response = mean(resp), .groups = "drop") %>%
  group_by(task, mov, unimodal, gain, Target_length) %>%
  summarise(
    mean = mean(response),
    se = sd(response) / sqrt(n()), # SE across subjects
    n = n(),
    .groups = "drop"
  )

# Plot
p1 <- ggplot(data = plotData %>% filter(unimodal == "Self-touch")) +
  geom_point(aes(x = Target_length, y = mean, color = gain), show.legend = F) +
  geom_line(aes(x = Target_length, y = mean, color = gain, group = gain), show.legend = F) +
  geom_ribbon(aes(
    x = Target_length, ymin = mean - se, ymax = mean + se,
    fill = gain, group = gain
  ), alpha = 0.15, show.legend = F) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(task ~ mov) +
  scale_x_continuous(limits = c(2, 10), breaks = seq(4, 8, by = 2)) +
  scale_y_continuous(limits = c(2, 10), breaks = seq(2, 10, by = 2)) +
  labs(
    title = "Self-touch Conditions",
    x = "Actual target extent (cm)", y = "",
    color = "Gain", fill = "Gain"
  ) +
  theme(
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )

p2 <- ggplot(data = plotData %>% filter(unimodal == "Unimodal")) +
  geom_point(aes(x = Target_length, y = mean, color = gain), show.legend = T) +
  geom_line(aes(x = Target_length, y = mean, color = gain, group = gain), show.legend = T) +
  geom_ribbon(aes(
    x = Target_length, ymin = mean - se, ymax = mean + se,
    fill = gain, group = gain
  ), alpha = 0.15, show.legend = T) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(task ~ mov, drop = T) +
  scale_x_continuous(limits = c(2, 10), breaks = seq(4, 8, by = 2)) +
  scale_y_continuous(limits = c(2, 10), breaks = seq(2, 10, by = 2)) +
  labs(
    title = "Unimodal Conditions",
    x = "Actual target extent (cm)", y = "Perceived target extent (cm)",
    color = "Gain", fill = "Gain"
  ) +
  theme(
    legend.position = c(.15, .9),
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.key = element_blank(),
    legend.background = element_rect(fill = "transparent"),
    legend.title = element_text(size = 16)
  )

grid.arrange(p2, p1, ncol = 2)
```

## Calculate Interference Coefficients
```{r ICs, fig.height= 7, fig.width= 7, warning=FALSE, message=FALSE, collapse = TRUE}
w <- shortData %>%
  filter(unimodal == "Self-touch") %>%
  # filter(gain != 1.25, gain != 0.8)  %>%
  group_by(sbjN, mov, task) %>%
  do({
    model <- lm(resp ~ 0 + touchLength + movLength, data = .)
    as.data.frame(t(coef(model)))
  }) %>%
  ungroup() %>%
  mutate(
    normTouch = touchLength / (movLength + touchLength),
    normMove = movLength / (movLength + touchLength),
    weights = case_when(
      task == "Judge Touch" ~ normMove,
      task == "Judge Movement" ~ normTouch
    )
  )

w$mov <- factor(w$mov, levels = c("Active", "Passive"))

wideW <- w %>%
  select(-c(touchLength, movLength, normTouch, normMove)) %>%
  pivot_wider(
    names_from = c(task, mov), # Columns to use for names
    values_from = c(weights), # Values to fill in the table
    names_sep = "_"
  )
# clipr::write_clip(wideW)

ggplot(w, aes(x = mov, y = weights, fill = interaction(mov, task))) +
  geom_bar(stat = "summary", show.legend = FALSE) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  facet_wrap(~task) +
  ylim(0, 1) +
  labs(
    x = "Condition",
    y = "Weigt of task-irrelevant information (ω)",
    title = "Mean Interference Weights (ω) \nAcross Movement and Judgment Conditions"
  ) +
  theme(
    aspect.ratio = 2,
    legend.position = "bottom",
    strip.text = element_text(size = 10),
    plot.title = element_text(size = 13),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12)
  )
```

## Run ANOVA
```{r Behavioral ANOVA, warning=FALSE, message=FALSE, collapse = TRUE}
full_ANOVA <- aov_ez(
  id = "sbjN",
  dv = "weights",
  within = c("mov", "task"),
  data = w,
  anova_table = list(correction = "GG", es = "pes") # request partial eta squared
)

# Use nice() to display the ANOVA table with effect sizes:
nice(full_ANOVA)
```

# EEG results
## Variable definition

  - **Estimation Error** quantifies *perceptual interference* with both positive and negative value, i.e., overestimation and negative estimation, respectively.
  
  $$estError = \frac{reported length}{target length}\ - 1$$
  
  - The balance of interhemispheric activity refers to the trial-level difference in beta power between C3 and C4 electrodes. It represents the degree to which motor activity interferes with tactile processing. 
  
  This beta power difference could be calculated for the raw beta power (μV^2) of C3 and C4 as: 

  $$\Delta{\beta_{raw}} = \beta_{C3(μV^2)}-\beta_{C4(μV^2)}$$

  A positive difference occurs when the absolute beta power is higher in the motor-related electrode C3 (tactile focus state of processing), while a negative difference occurs when beta power in the tactile-related electrode C4 (motor focus state). 
  
  Optional: Because raw EEG power is positively skewed, we applied the subtraction with the log-normalized beta power (dB) to satisfy the requirement for a Normal distributed predictor. The difference in log-transformed beta power could be expressed as beta power log-ratio:
  
  $$\Delta{\beta_{dB}} = \beta_{C3(dB)}-\beta_{C4(dB)}= 10 \times log_{10}\beta_{C3(μV^2)}-10 \times log_{10}\beta_{C4(μV^2)} =10 \times log_{10}{\frac{\beta_{C3(μV^2)}}{\beta_{C4(μV^2)}}}$$

  
Unlike the absolute power difference, a positive ratio value such as +10 dB would mean the beta power in channel C3 is 10 times the power in channel C3, suggests a stronger focus on tactile processing, while a negative difference is associated with less beta power in channel C3, indicating a stronger motor processing. By using the difference of logs, the log-ratio index additionally ensures that the proportional changes in interhemispheric balance are treated symmetrically by the statistical model.

**This script will use beta `r predictor.name` as the continuous predictor for estimation error.**

<p style="text-align: justify;">

## ERD variability

Check for ERD/S: Relative to the baseline (before movement), we see a drop (ERD) in beta power amplitude in early movement and a rebound (ERS) after movement stops (after movement).

```{r ERD Plots, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
plotData <- longData %>%
  filter(unimodal == "Unimodal" & timing != "Full Movement") %>%
  group_by(condN, timing, relativehemisphere, location) %>%
  get_summary_stats(powerBeta)
# summarise(powerBeta=mean(powerBeta))

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN), size = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), size = 1) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), size = 2) +
  facet_wrap(~relativehemisphere) +
  scale_color_manual("Condition", values = palette$three.color2) +
  labs(
    title = "Beta Power in unimodal conditions at contra-lateral hemisphere",
    x = "Movement Phases",
    # y = expression(paste("x axis ", ring(A)^2)),
    y = expression(paste("Averaged ", Beta, " power (", mV^2, ")"))
  ) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )


plotData <- byBaseline.longData %>%
  filter(unimodal == "Unimodal" & timing != "Full Movement") %>%
  group_by(condN, timing, relativehemisphere, location) %>%
  get_summary_stats(powerBeta)

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN), size = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), size = 1) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), size = 2) +
  facet_wrap(~relativehemisphere) +
  scale_color_manual("Condition", values = palette$three.color2) +
  labs(
    title = "Beta ERD in unimodal conditions at contra-lateral hemisphere",
    x = "Movement Phases",
    y = "Relative Power Change (%)"
  ) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )
```




## Self-touch: Interhemispheric interference
**Does the relative difference in beta power between channel C3 and C4 during self-touch explain the asymmetrical, bidirectional interference of movement and tactile spatial percepts?**

**Does interhemispheric balance predict how accurate participants are around the target?**
H: Negative difference in the beta power between the channels C3 and C4 [C3-C4] (i.e., stronger motor processing than tactile processing) is associated with smaller error in move judgement and larger error in touch judgement.

```{r Data for the model, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
filter.timing <- "Full"
predictData <- parData %>%
  filter(flipped.gain != "1.Unity" & unimodal == "Self-touch" & timing == paste(filter.timing, "Movement")) %>%
  mutate(sbjN = factor(sbjN)) %>%
  mutate(
    estError = (resp - Target_length) / Target_length,
    GAIN = flipped.gain
  )
```


One could fit a linear mixed-effects model of the fixed effects including 

- [1] **interhemispheric balance**: trial-level difference in beta power between C3 and C4 electrodes. A positive difference is associated with a focus on tactile processing, and a negative difference is associated with stronger motor processing 

- [2] **task**: Judge Touch (reference) vs Judge Movement

- [3] **movement type**: Passive (reference) vs Active]

- [4] **non-unity gain**: Move < Touch (i.e., 1:1.5, reference) vs Move > Touch (i.e., 1.5:1) 

```{r Coding scheme 1A, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE, eval = FALSE, include = TRUE} 
# # CODING APPROACH 1: DUMMY CODING
# # 1. Set Passive as the Reference
# # Assuming "Passive" is the first (reference) level
# predictData$mov <- relevel(predictData$mov, ref = "Passive")
# (contrasts(predictData$mov) <- contr.treatment(2))
# 
# # 2. Set Touch as reference
# (contrasts(predictData$task) <- contr.treatment(2))
# 
# # 3. Set Gain contr.treatment(2)
# predictData$gain <- factor(predictData$gain, levels = c("Move < Touch", "Move > Touch"))
# (contrasts(predictData$gain) <- contr.treatment(2))

```


We could also use a mixed coding approach to facilitate the interpretation of our theoretical factors as following: 

- [1] **interhemispheric balance**: trial-level Beta `r predictor.name`` between C3 and C4 electrodes. A positive difference is associated with a focus on tactile processing, and a negative difference is associated with stronger motor processing 

- [2] **task**: Judge Touch (reference) vs Judge Movement

- [3] **movement type**: Passive (reference) vs Active]

- [4] **non-unity gain**: Move < Touch (i.e., 1:1.5, reference) vs Move > Touch (i.e., 1.5:1) 


Movement type was dummy-coded to treat the Passive condition as the reference level. The model coefficients for the Active condition could quantify the changes in judgement induced by the presence of an efferent copy of the motor command. Task and gain are sum-coded to account for their distinct qualitative nature arising from different modalities and symmetrical spatial decoupling, respectively. Sum coding is chosen to represent deviations from the experimental mean. Post-hoc comparisons and slope estimates were derived using the emmeans package. 

We assume that judging touch and judging movement are equivalent tasks, as well as no effect of modality on gain. Therefore, we apply for a mixed coding approach that kept the dummy coding of movement type (i.e., Passive condition as reference level) and sum-coded task (Judge Touch vs Judge Movement) and gain. 

```{r Coding scheme 1B, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# CODING APPROACH 2: MIXED CODING APPROACH
# 1. Set Passive as the Reference (Dummy Coding)
# Assuming "Passive" is the first level alphabetically; if not, use relevel()
predictData$mov <- relevel(predictData$mov, ref = "Passive")
contrasts(predictData$mov) <- contr.treatment(2)

# 2. Set Touch vs Move as Sum Coding (Effect Coding)
contrasts(predictData$task) <- contr.sum(2)

# 3. Set Gain as Sum Coding (Effect Coding)
predictData$gain <- factor(predictData$gain, levels = c("Move < Touch", "Move > Touch"))
contrasts(predictData$gain) <- contr.sum(2)

```


### Linear Mixed Model

For the model, we included a random intercept for subject to account for repeated measures within participants.

```{r LMER, fig.width=10, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# LINEAR MIXED MODEL
# Predicting Estimation Error based on the 4-way interaction of Beta Power Ratio,
# Task, Movement Type, and Gain, with random intercepts for Subjects

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov * gain + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
summary_df <- as.data.frame(summary(model)$coefficients) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  rownames_to_column("factor") %>%
  mutate(factor = factor %>%
    str_replace_all("PowerDiff", predictor.name) %>%
    str_replace_all("task1", "Task [JudgeTouch]") %>%
    str_replace_all("task2", "Task [JudgeMove]") %>%
    str_replace_all("mov1", "Movement [Passive]") %>%
    str_replace_all("mov2", "Movement [Active]") %>%
    str_replace_all("gain1", "Gain [M<T]") %>%
    str_replace_all("gain2", "Gain [M>T]") %>%
    str_replace_all(":", " × "))

xlsx_name <- sprintf("lmer_results_%s_%s.xlsx", power.type, script_time)
xlsx::write.xlsx(
  x = summary_df %>%
    mutate(across(where(is.numeric), ~ format(.x, decimal.mark = "."))),
  sheetName = "p1B_lmer",
  file = file.path(
    pathlist$result_path,
    xlsx_name
  ), append = TRUE
)

# Anova result
anova.model <- anova(model)
print(anova.model)

rownames(anova.model) <- rownames(anova.model) %>%
  str_replace_all("PowerDiff", predictor.name) %>%
  str_replace_all("task", "Task") %>%
  str_replace_all("mov", "Movement") %>%
  str_replace_all("gain", "Gain") %>%
  str_replace_all(":", " × ")

xlsx_name <- sprintf("lmer_results_%s_%s.xlsx", power.type, script_time)
xlsx::write.xlsx(
  x = anova.model %>% round(3) %>%
    mutate(across(where(is.numeric), ~ format(.x, decimal.mark = "."))),
  sheetName = "p1B_anova",
  file = file.path(
    pathlist$result_path,
    xlsx_name
  ), append = TRUE
)

# Generate predictions for PowerDiff across task, mov, and gain
pred <- ggpredict(model, terms = c("PowerDiff [all]", "task", "mov", "gain"))

x_axis <- ifelse(power.type == "raw",
  expression(paste("Beta Power Difference (", mV^2, ")")),
  ifelse(power.type == "log",
    expression(paste("Beta Power Log-Ratio (dB)"))
  )
)
# Plot predictions
p0 <- ggplot(pred, aes(x = x, y = predicted, color = group)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  annotate("text", x = -.5, y = +Inf, label = sprintf("\u2190\u2190\u2190\nmotor-focused"), color = palette$two.color1[2], hjust = 1, vjust = "top", size = 12 / .pt) +
  annotate("text", x = +.5, y = +Inf, label = sprintf("\u2192\u2192\u2192\ntactile-focused"), color = palette$two.color1[1], hjust = 0, vjust = "top", size = 12 / .pt) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2) +
  facet_grid(facet ~ panel) + # Adjust based on ggpredict output (mov × gain)
  labs(
    title = paste("Predicting Estimation Error with Beta Power during", filter.timing, "Self-touch"),
    subtitle = paste0("Beta", predictor.name, " x Task x Movement type x Gain"),
    x = x_axis,
    y = "Estimation Error\n(-1 = underestimation, 0 = accurate, +1 =overestimation)\n"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_fill_manual("Task", values = palette$two.color1) +
  theme(
    aspect.ratio = 1,
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
p0
```


### Post hoc: Slope analysis

We now estimate the specific relationship (slope) between Beta Power and Estimation Error across Task, Movement, and Gain conditions to clarify the multiple interactions. 

First slope analysis: Movement effect (Passive vs Active)
```{r Post hoc Slope 1, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# POST HOC 1: Slope analysis
# Testing Slopes: Movement effect (Passive vs Active)
cs <- emtrends(model, pairwise ~ mov, var = "PowerDiff")
css <- summary(cs)
print(css$contrasts)
print(css$emtrends)


```



Second slope analysis: Task x Gain interaction
```{r Post hoc Slope 2, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Testing Slopes: Task x Gain interaction
cs <- emtrends(model, pairwise ~ task * gain, var = "PowerDiff")
css <- summary(cs)
print(css$contrasts)
print(css$emtrends)
```



Third slope analysis: Movement by combi of Task x Gain interaction
```{r Post hoc Slope 3, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 

# Testing Slopes: MoV in different Task x Gain interaction
cs <- emtrends(model, pairwise ~ mov | task * gain, var = "PowerDiff")
css <- summary(cs)
print(css$contrasts)
print(css$emtrends)

```



Forth slope analysis: Move x Task x Gain interaction
```{r Post hoc Slope 4, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 

# Testing Slopes: MoV in different Task x Gain interaction
cs <- emtrends(model, pairwise ~ task * gain * mov, var = "PowerDiff")
css <- summary(cs)
print(css$contrasts %>% arrange(p.value))
print(css$emtrends)
```


### Post hoc 2:  Estimated Marginal Mean (EMM)

**Additional investigation**: In the condition $\text{Judge Movement}:\text{Passive}:\text{Move > Touch}$, is the predicted estimation error ($\text{estError}$) equal to zero when the neural predictor ($\text{PowerDiff}$) is exactly zero?

- The Statistical Test: Contrasting the Estimated Marginal Mean (EMM) against Zero

- The $\text{emmeans}$ function can calculate the predicted mean of the dependent variable ($\text{estError}$) for any specific combination of factors, holding continuous predictors (like $\text{PowerDiff}$) at a specific value (e.g., zero).

```{r Against 0, fig.width=10, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Step 1: Calculate the EMM at PowerDiff = 0
emm_at_zero <- emmeans(model,
  specs = ~ task * mov * gain,
  at = list(PowerDiff = 0)
)
emm_table = summary(emm_at_zero) %>% arrange(lower.CL,upper.CL)
print(emm_table)

xlsx_name <- sprintf("lmer_results_%s_%s.xlsx", power.type, script_time)
xlsx::write.xlsx(
  x = emm_table,
  sheetName = "p1B_emm_table",
  file = file.path(
    pathlist$result_path,
    xlsx_name
  ), append = TRUE
)
# Step 2: Test the Hypothesis ($\text{Estimate} = 0$)
# Test the specific estimate against zero
test_result <- contrast(emm_at_zero, 
                        method = "revpairwise",
                        by = "task",
                        adjust = "Tukey"
) # Use adjust="none" or "Tukey" as needed

test_df = test_result %>% as.data.frame()
print(test_df)
# Filter the contrast output for the test: "Estimate vs. 0"
# (Note: Often, if the CI from Step 1 does not include zero, the test is redundant)


xlsx::write.xlsx(
  x = test_df,
  sheetName = "p1B_emm_contrast",
  file = file.path(
    pathlist$result_path,
    xlsx_name
  ), append = TRUE
)

# Step 3: Plot EMMs
library(tidyverse)

# Assuming your summary table is named 'emm_table'
emm_table <- emm_table %>%
  mutate(
    # Define the Relationship based on Task and Gain
    relationship = case_when(
      task == "Judge Touch"    & gain == "Move > Touch" ~ "Target < Interference",
      task == "Judge Touch"    & gain == "Move < Touch" ~ "Target > Interference",
      task == "Judge Movement" & gain == "Move > Touch" ~ "Target > Interference",
      task == "Judge Movement" & gain == "Move < Touch" ~ "Target < Interference"
    ),
    # Define if the estimate is statistically different from zero
    Status = case_when(
      lower.CL > 0 ~ "Overestimation",
      upper.CL < 0 ~ "Underestimation",
      TRUE         ~ "Accurate"
    )
  ) %>%
  arrange(task,mov, relationship)

p0 <- ggplot(data = emm_table)+
  geom_point(aes(x= "", y= emmean, color = task))+
  geom_errorbar(aes(x= "", ymin=emmean-SE, ymax=emmean+SE, color = task))+
  facet_grid(mov~gain, drop = TRUE)+ 
  labs(
    title = paste("Estimation Error at with Beta Power Difference = 0 ", filter.timing, "Self-touch"),
    subtitle = paste0("Beta", predictor.name, " x Task x Movement type x Gain"),
    x = "Movement type",
    y = "Estimation Error\n(-1 = underestimation, 0 = accurate, +1 =overestimation)\n"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_fill_manual("Task", values = palette$two.color1) +
  theme(
    aspect.ratio = 1,
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
p0
```

The most important finding here is which conditions are not biased when the neural predictor is neutral. This demonstrates where the behavioral effects of $\text{task}$, $\text{mov}$, and $\text{gain}$ effectively cancel each other out:

- Four conditions show NO significant bias at symmetrical processing ($\text{PowerDiff}=0$). This is quite powerful, as it suggests the behavioral effects of the sensory context are not a sufficient explanation for bias in these cases; the bias must be driven by the neural modulation ($\text{PowerDiff}$ interaction).

- Four conditions do show a significant bias, meaning the combined effects of $\text{task}$, $\text{mov}$, and $\text{gain}$ create an inherent bias that the neural state must counteract or enhance.
