---
title: "TOUCH-BRAIN: Pre-Registration Plan"
author: "Phuc TU Nguyen"
date: "2025-06-06"

output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    toc: true
    toc_depth: 3
    number_sections: true
    collapse: true
---

```{r setup, warning=FALSE, echo=FALSE, message=FALSE}
## Set up libraries and define paths with function

rm(list = ls())
library(rstudioapi)

script_path <- dirname(rstudioapi::getActiveDocumentContext()$path)
function_path <- file.path(script_path, "function")

source(file.path(function_path, "loadconfig.R"))
load_lib()
load_path(script_path)
load_palette()

phases <- c(
  "Movement Cue",
  "Before Movement",
  "During Movement",
  "Early Movement", "Half Movement", "Late Movement", "Full Movement",
  "After Movement"
)
vps <- c("P")
```


# Pool data {.hidden .unlisted}
<font size="1"> Behavioral and EEG data are merged across all participants and blocks. Block number and trial number are assigned per condition (t/m &times; a/p &times; unimodal/both) </font>

```{r warning=FALSE, message=FALSE, echo=FALSE}
source(file.path(function_path, "loaddata.R"))

# BEH ----
beh_combined_df <- load_behdata(vps, pathlist$beh_data_path)
beh_combined_df <- adjust_beh_df(beh_combined_df)
# Test for sufficient blocks
beh_test <- beh_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial_beh = n(), .groups = "drop")

# EEG ----
eeg_combined_df <- load_eegdata(vps, file.path(pathlist$eeg_data_path, "Revise_5Phase"))

# Adjustment according to protocol
{
  empty_row <- eeg_combined_df[1, ]
  empty_row[1, ] <- NA

  empty_row$filename <- "P23_move_active_results.xls"
  eeg_combined_df <- rbind(
    eeg_combined_df[1:(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[36]), ],
    empty_row,
    eeg_combined_df[(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[37]):nrow(eeg_combined_df), ]
  )
  eeg_combined_df <- eeg_combined_df[-which(eeg_combined_df$filename == "P23_move_passive_results.xlsx")[51], ]
}


eeg_combined_df <- adjust_eeg_df(eeg_combined_df)

# Test for sufficient blocks
eeg_test <- eeg_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial = n(), .groups = "drop")

# Compare trial counts between behavioral and EEG data
testmerge <- left_join(beh_test, eeg_test,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal")
) %>%
  arrange(NAME, unimodal, QUESTION, ACTIVE) %>%
  mutate(trialdiff = ntrial_beh - ntrial)
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
# Merge full behavioral and EEG datasets
merge_df <- left_join(beh_combined_df, eeg_combined_df,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal", "trial_number")
)

# Compare trial counts between behavioral and EEG data
testmerge1 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())
```

```{r fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# Remove specific blocks for specific subjects
merge_df <- merge_df %>%
  filter(!(NAME == "P03" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "p" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P17" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P22" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P23" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "p" & trial_number %in% c(50))) %>%
  filter(!(NAME == "P25" & !is.na(unimodal) & unimodal == "1" & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(1))) %>%
  # temporary filter due to unsatisfactory preprocessing
  filter(!(NAME %in% c("P11", "P17", "P22")))

testmerge2 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

testmerge3 <- merge_df %>%
  mutate(
    NAME = str_extract(NAME, "\\d+") %>% as.numeric(),
    unimodal = case_when(
      unimodal %in% c("1", "2") ~ "Unimodal",
      !unimodal %in% c("1", "2") ~ "Self_touch"
    )
  ) %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

ggplot(testmerge3) +
  geom_point(aes(x = NAME, y = n, color = unimodal)) +
  facet_wrap(QUESTION ~ ACTIVE) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  labs(
    title = "Check for data completeness - Before Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  ) +
  theme(
    # legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 18)
  )
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
# Export merged data to Excel
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
write_xlsx(merge_df, file.path(pathlist$result_path, xlsx_name))
# print(codebookr::codebook(rawData), file.path(pathlist$result_path,"ST_EEG_Codebook.docx"))

rm(list = c(
  "beh_combined_df", "beh_test",
  "eeg_combined_df", "eeg_test",
  "empty_row",
  "merge_df",
  ls(pattern = "^test")
))
```


## Load and preprocess raw data 
```{r warning=FALSE, message=FALSE, echo=FALSE}
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
source(file.path(function_path, "preprocessdata.R"))
# channels <- expand.grid(c("F", "Fc", "FC", "C", "CP", "P"), c("3", "5", "z", "4", "6"))
channels <- expand.grid(c("C"), c("3", "4"))
channels <- paste0(channels$Var1, channels$Var2)
```

**Target Length**: based on the task type (touchLength or movLength is selected).

**Condition Labels (condN)**: (1) Self-touch Active - Judge Touch, 
(2) Self-touch Passive - Judge Touch, 
(3) Self-touch Active - Judge Move, 
(4) Self-touch Passive - Judge Move*, 
(5) Unimodal - Judge Touch, 
(6) Unimodal Active - Judge Move, 
(7) Unimodal Passive - Judge Move. 

**Flipped Gain**: Calculated as $|\frac{TargetLength}{InterferenceLength}\ |$.

**Absolute Error**: Calculated as $|\frac{ReportedLength}{TargetLength}\ - 1|$.

```{r layout="l-body-outset", fig.width=4, fig.height=4, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
rawData <- read_excel(path = file.path(pathlist$result_path, xlsx_name))
rawData <- preprocess_beh_df(rawData) %>%
  select(
    sbjN, trialN, task, mov, unimodal, condN, BLOCK, trial_number, DURATION, MovDur, HalfDur,
    gain, flipped.gain, touchLength, movLength, Target_length, Interference_length, resp, estError, absError, delta,
    starts_with(channels)
  )

rawData %>%
  select(
    sbjN, condN, BLOCK, trialN, flipped.gain, Target_length, resp,
    matches("^(C3|C4).*_(pre|full|early|late)$")
  ) %>%
  arrange(sbjN, condN, BLOCK, trialN) %>%
  rmarkdown::paged_table(options = list(rows.print = 10, cols.print = 9))
```

```{r fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# EEG ----
# Make long data
rawData.filter <- filter_outliers(
  df = rawData %>% mutate(puffer = 1 %>% as.factor()),
  value_col = "resp", group_cols = c("puffer")
) # filter extreme response
ggplot(rawData) +
  geom_histogram(aes(x = resp)) +
  scale_x_continuous("Response", limits = c(0, 20), breaks = seq(0, 20, 10)) +
  labs(title = "Response distribution before filtering out outliers")
ggplot(rawData.filter) +
  geom_histogram(aes(x = resp)) +
  scale_x_continuous("Response", limits = c(0, 20), breaks = seq(0, 20, 10)) +
  labs(title = "Response distribution after filtering out outliers")

ggplot(rawData.filter) +
  geom_histogram(aes(x = MovDur)) +
  scale_x_continuous("Move Duration (s)", limits = c(0, 10), breaks = seq(0, 20, 10)) +
  labs(title = "Distribution of Moving Duration (excluded: more than 8s)")


longrawData <- long_beh_eeg_df(rawData.filter)
longData <- filter_outliers(df = longrawData, value_col = "powerBeta", group_cols = c("channellocation_timing")) # filter extreme Beta power values

ggplot(longrawData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5) +
  facet_wrap(~timing)+
  labs(title = "Distribution of Beta Power before filtering out outliers")

ggplot(longData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5) +
  facet_wrap(~timing)+
  labs(title = "Distribution of Beta Power before filtering out outliers")


shortData <- short_beh_eeg_df(longData %>% select(sbjN:powerBeta)) %>%
  mutate(unimodal = as.factor(unimodal))

testmerge4 <- shortData %>%
  mutate(sbjN = str_extract(sbjN, "\\d+") %>% as.numeric()) %>%
  group_by(sbjN, task, mov, unimodal) %>%
  summarise(n = n())

ggplot(testmerge4) +
  geom_point(aes(x = sbjN, y = n, color = unimodal)) +
  facet_wrap(task ~ mov) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  labs(
    title = "Check for data completeness - After Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )


# To calculate change of Beta power
# present data frame_ one column for C3, one column for C4
parData <- longData %>%
  select(sbjN:delta, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

byBaseline.shortData <- shortData %>%
  select(sbjN:absError, starts_with("C3"), starts_with("C4")) %>%
  rowwise() %>%
  mutate(
    C3_full = 100 * (C3_full - C3_pre) / C3_pre,
    C4_full = 100 * (C4_full - C4_pre) / C4_pre,
    C3_early = 100 * (C3_early - C3_pre) / C3_pre,
    C4_early = 100 * (C4_early - C4_pre) / C4_pre,
    C3_late = 100 * (C3_late - C3_pre) / C3_pre,
    C4_late = 100 * (C4_late - C4_pre) / C4_pre
  ) %>%
  mutate(C3_pre = 0, C4_pre = 0)


byBaseline.longData <- long_beh_eeg_df(byBaseline.shortData)

# Create a unique trial ID in both datasets
longData <- longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

byBaseline.longData <- byBaseline.longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

# Filter byBaseline.longData to keep only rows present in longData - remove outliers based off the raw power Beta
byBaseline.longData <- byBaseline.longData %>%
  filter(trialID %in% longData$trialID)


byBaseline.parData <- byBaseline.longData %>%
  select(sbjN:absError, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)
```


# Research questions
## Self-touch: Interhemispheric interference
### Basic analyses

  - **Judgement Error** quantifies *perceptual interference* with both positive and negative value, i.e., overestimation and negative estimation, respectively.
  
  $$Judgement Error = \frac{reported length}{true length}\ - 1$$
  
  - **ABSOLUTE Judgement Error** quantifies *perceptual interference* without negative value, i.e., the degree to which the perceptual judgement deviates from the true value OR how much the perceptual judgement is interfered by other information.
  
  $$ABSOLUTE Judgement Error = |JudgementError| = |\frac{reported length}{true length}\ - 1|$$
  
  - **Beta Power Difference** between the left hemisphere (C3) and the right hemisphere (C4) represents the degree to which motor activity interferes with tactile processing. Positive difference implies weaker interference of motor information (tactile focus), while negative difference implies stronger interference of motor information (motor focus).
  
  $$\Delta{B} = B_{C3} - B_{C4}$$
  

Because movement and tactile spatial percepts during self-touch are interfered by the processing of tactile and movement information, respectively, we expect that the neural marker of these two components could be used to predict judgement accuracy. For example, a negative difference in beta power between C3 and C4 *(C3 - C4)* reflects larger processing of motor information relative to tactile information and may suggest that motor information is weighted more in length judgement than tactile judgement

<p style="text-align: justify;">

**Q6: (Self-touch conditions) Does the relative difference in beta power between channel C3 and C4 during self-touch explain the asymmetrical, bidirectional interference of movement and tactile spatial percepts?**

H6: Negative difference in the beta power between the channels C3 and C4 [C3-C4] (i.e., stronger motor processing than tactile processing) is associated with smaller error in move judgement and smaller tactile judgement.

#### Absolute Error

```{r fig.width=16, fig.height=10, echo=FALSE, warning=FALSE, message=FALSE} 
# Raw Beta power ---------------
## Absolute error ----

plotData <- parData %>% filter(unimodal == "Self-touch" & flipped.gain != "1.Unity")

ggplot(
  plotData,
  aes(x = PowerDiff, y = absError, color = task)
) +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Non-Unity Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "ABSOLUTE Judgement Error"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(mov ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- parData %>%
  filter(unimodal == "Self-touch" & flipped.gain != "1.Unity" & timing %in% c("Full Movement")) %>%
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```

```{r fig.width=12, fig.height=12, echo=FALSE, warning=FALSE, message=FALSE}
# plotData <- parData %>% filter(unimodal == "Self-touch" & mov = "Active")
# 
# ggplot(
#   plotData,
#   aes(x = PowerDiff, y = absError, color = task)
# ) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   geom_vline(xintercept = 0, linetype = "dashed") +
#   geom_point(alpha = .05, show.legend = F) +
#   geom_smooth(method = "lm", show.legend = T) +
#   labs(
#     title = "Predicting Judgement Error with Difference of Beta Power (Active Conditions)",
#     x = "Beta Power Difference: C3 - C4",
#     y = "ABSOLUTE Judgement Error"
#   ) +
#   scale_color_manual("Task", values = palette$two.color1) +
#   scale_x_continuous(limits = c(-6.5, 5.5)) +
#   # scale_y_continuous(limits = c(-1, 2.5))+
#   facet_wrap(gain ~ timing, nrow=2) +
#   theme(
#     legend.position = "bottom",
#     strip.text = element_text(size = 16),
#     plot.title = element_text(size = 19),
#     axis.text = element_text(size = 18),
#     axis.title = element_text(size = 18)
#   )
# 
# plotData <- parData %>% filter(unimodal == "Self-touch" & mov = "Passive")
# 
# ggplot(
#   plotData,
#   aes(x = PowerDiff, y = absError, color = task)
# ) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   geom_vline(xintercept = 0, linetype = "dashed") +
#   geom_point(alpha = .05, show.legend = F) +
#   geom_smooth(method = "lm", show.legend = T) +
#   labs(
#     title = "Predicting Judgement Error with Difference of Beta Power (Passive conditions)",
#     x = "Beta Power Difference: C3 - C4",
#     y = "ABSOLUTE Judgement Error"
#   ) +
#   scale_color_manual("Task", values = palette$two.color1) +
#   scale_x_continuous(limits = c(-6.5, 5.5)) +
#   # scale_y_continuous(limits = c(-1, 2.5))+
#   facet_wrap(gain ~ timing, nrow = 2) +
#   theme(
#     legend.position = "bottom",
#     strip.text = element_text(size = 16),
#     plot.title = element_text(size = 19),
#     axis.text = element_text(size = 18),
#     axis.title = element_text(size = 18)
#   )
# 
# predictData <- parData %>%
#   filter(flipped.gain != "1.Unity" & unimodal == "Self-touch" & timing %in% c("Full Movement")) %>%
#   mutate(sbjN = factor(sbjN))
# 
# # Fit the linear mixed model
# model <- lmer(absError ~ PowerDiff * task * mov * gain + (1 | sbjN), data = predictData)
# 
# # View the summary of the model
# summary(model)
```



#### Signed Error

```{r fig.width=16, fig.height=10, echo=FALSE, warning=FALSE, message=FALSE} 
## Signed error ----

plotData <- parData %>% filter(unimodal == "Self-touch" & flipped.gain != "1.Unity")

ggplot(
  plotData,
  aes(x = PowerDiff, y = estError, color = task)
) +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Non-Unity Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "ABSOLUTE Judgement Error"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(mov ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- parData %>%
  filter(unimodal == "Self-touch" & flipped.gain != "1.Unity" & timing %in% c("Full Movement")) %>%
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=12, fig.height=12, echo=FALSE, warning=FALSE, message=FALSE}

plotData <- parData %>% filter(unimodal == "Self-touch" & flipped.gain!="1.Unity")

ggplot(
  plotData,
  aes(x = PowerDiff, y = estError, color = task)
) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  labs(
    title = "Will it be cancelled out? - Predicting Judgement Error with Difference of Beta Power",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-6.5, 5.5)) +
  scale_y_continuous(limits = c(-1, 2.5)) +
  facet_wrap(gain~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )


plotData <- parData %>% filter(unimodal == "Self-touch" & flipped.gain!="1.Unity" & mov == "Active")

ggplot(
  plotData,
  aes(x = PowerDiff, y = estError, color = task)
) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Active Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-6.5, 5.5)) +
  scale_y_continuous(limits = c(-1, 2.5)) +
  facet_wrap(gain ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

plotData <- parData %>% filter(unimodal == "Self-touch" & flipped.gain!="1.Unity" & mov == "Passive")

ggplot(
  plotData,
  aes(x = PowerDiff, y = estError, color = task)
) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Passive Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-6.5, 5.5)) +
  scale_y_continuous(limits = c(-1, 2.5)) +
  facet_wrap(gain ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- parData %>%
  filter(gain != "Move = Touch" & unimodal == "Self-touch" & timing %in% c("Full Movement")) %>%
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov * gain + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=16, fig.height=10, echo=FALSE, warning=FALSE, message=FALSE}
# %change Beta power -------
## Absolute error ----

plotData <- byBaseline.parData %>% filter(unimodal == "Self-touch" & gain != "Move = Touch")

ggplot(
  plotData,
  aes(x = PowerDiff, y = absError, color = task)
) +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Predicting with the relative degree of ERD",
    x = "Beta ERD Difference: C3 - C4",
    y = "ABSOLUTE Judgement Error"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(mov ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- byBaseline.parData %>%
  filter(unimodal == "Self-touch" & gain != "Move = Touch" & timing %in% c("Full Movement")) %>%
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=12, fig.height=12, echo=FALSE, warning=FALSE, message=FALSE}
plotData <- byBaseline.parData %>% filter(unimodal == "Self-touch" & mov == "Active")

ggplot(
  plotData,
  aes(x = PowerDiff, y = estError, color = task)
) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Active Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-755, 600)) +
  scale_y_continuous(limits = c(-1, 2.5)) +
  facet_wrap(gain ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

plotData <- byBaseline.parData %>% filter(unimodal == "Self-touch" & mov == "Passive")

ggplot(
  plotData,
  aes(x = PowerDiff, y = estError, color = task)
) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Passive Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-755, 600)) +
  scale_y_continuous(limits = c(-1, 2.5)) +
  facet_wrap(gain ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- parData %>%
  filter(unimodal == "Self-touch" & timing %in% c("Full Movement") & gain != "Move = Touch") %>%
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov * gain + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=12, fig.height=12, echo=FALSE, warning=FALSE, message=FALSE}
## signed error ----
plotData <- byBaseline.parData %>% filter(unimodal == "Self-touch" & mov == "Active")

ggplot(
  plotData,
  aes(x = PowerDiff, y = estError, color = task)
) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Active Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-755, 600)) +
  scale_y_continuous(limits = c(-1, 2.5)) +
  facet_wrap(gain ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

plotData <- byBaseline.parData %>% filter(unimodal == "Self-touch" & mov == "Passive")

ggplot(
  plotData,
  aes(x = PowerDiff, y = estError, color = task)
) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = T) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Passive Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-755, 600)) +
  scale_y_continuous(limits = c(-1, 2.5)) +
  facet_wrap(gain ~ timing, nrow = 2) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- parData %>%
  filter(unimodal == "Self-touch" & timing %in% c("Full Movement") & gain != "Move = Touch") %>%
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov * gain + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```
