---
title: "Selftouch EEG - Manuscript"
author: "Phuc TU Nguyen"
date: "2025-06-06"

output:
  html_document:
    theme: flatly       
    highlight: tango     # Nice syntax highlighting for R code
    toc: true
    toc_depth: 4
    toc_float: 
      collapsed: false   # Keeps the TOC expanded
      smooth_scroll: true
    number_sections: true
    code_folding: hide   
    df_print: paged      # Makes large data frames look like neat tables
---

```{r setup, warning=FALSE, echo=FALSE, message=FALSE}
## Set up libraries and define paths with function

rm(list = ls())
library(rstudioapi)

script_path <- dirname(rstudioapi::getActiveDocumentContext()$path)
function_path <- file.path(script_path, "function")

source(file.path(function_path, "loadconfig.R"))
load_lib()
load_path(script_path)
load_palette()

script_time <- format(Sys.time(), ("%d%m%Y_%H%M"))

phases <- c(
  "Movement Cue",
  "Before Movement",
  "During Movement",
  "Early Movement", "Half Movement", "Late Movement", "Full Movement",
  "After Movement"
)
vps <- c("P")
Target.interference.analysis = TRUE
power.type <- c("raw", "log", "log_of_difference")[2] # change format of Beta power

if (power.type == "raw") {predictor.name = "Power Difference"} else
  if (power.type == "log") {predictor.name = "Power Log-Ratio"} else
  if (power.type == "log_of_difference") {predictor.name = "Power Difference (log-transformed)"}

if (Target.interference.analysis == T) {
  predictor.name = paste(predictor.name, "[Target - Interference]")
  positive.label = "stronger interference"
  negative.label = "weaker interference"} else
  if (Target.interference.analysis == F) {
    predictor.name = paste(predictor.name, "[C3-C4]")
    positive.label = "tactile-focused"
    negative.label = "motor-focused"} 

preload.data = TRUE
```


# Pool and preprocess data

Behavioral and EEG data are merged across all participants and blocks. Block number and trial number are assigned per condition (t/m &times; a/p &times; unimodal/self-touch)


```{r Pool beh, warning=FALSE, message=FALSE, echo=FALSE, eval=!preload.data}
source(file.path(function_path, "loaddata.R"))

beh_combined_df <- load_behdata(vps, pathlist$beh_data_path)
beh_combined_df <- adjust_beh_df(beh_combined_df)
# Test for sufficient blocks
beh_test <- beh_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial_beh = n(), .groups = "drop")
```

```{r Pool eeg, warning=FALSE, message=FALSE, echo=FALSE, eval=!preload.data}
eeg_combined_df <- load_eegdata(vps, file.path(pathlist$eeg_data_path, "Revise_5Phase"))

# Adjustment according to protocol
{
  empty_row <- eeg_combined_df[1, ]
  empty_row[1, ] <- NA

  empty_row$filename <- "P23_move_active_results.xls"
  eeg_combined_df <- rbind(
    eeg_combined_df[1:(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[36]), ],
    empty_row,
    eeg_combined_df[(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[37]):nrow(eeg_combined_df), ]
  )
  eeg_combined_df <- eeg_combined_df[-which(eeg_combined_df$filename == "P23_move_passive_results.xlsx")[51], ]
}


eeg_combined_df <- adjust_eeg_df(eeg_combined_df)


# Test for sufficient blocks
eeg_test <- eeg_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial = n(), .groups = "drop")

# Compare trial counts between behavioral and EEG data
testmerge <- left_join(beh_test, eeg_test,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal")
) %>%
  arrange(NAME, unimodal, QUESTION, ACTIVE) %>%
  mutate(trialdiff = ntrial_beh - ntrial)
```

```{r Merge beh and eeg data, warning=FALSE, message=FALSE, echo=FALSE, eval=!preload.data}
# Merge full behavioral and EEG datasets
merge_df <- left_join(beh_combined_df, eeg_combined_df,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal", "trial_number")
)

# Compare trial counts between behavioral and EEG data
testmerge1 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())
```

```{r Remove data, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE, eval=!preload.data}
# Remove specific blocks for specific subjects
merge_df <- merge_df %>%
  filter(!(NAME == "P03" & is.na(unimodal) & QUESTION == "t" & ACTIVE == "p" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P17" & is.na(unimodal) & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P22" & is.na(unimodal) & QUESTION == "t" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P23" & is.na(unimodal) & QUESTION == "m" & ACTIVE == "p" & trial_number %in% c(50))) %>%
  filter(!(NAME == "P25" & !is.na(unimodal) & unimodal == "1" & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(1))) %>%
  # EEG preprocessing protocol: 
  # channel rejection: C3 or C4 
  filter(!(NAME %in% c("P20"))) %>%
  # low ICA quality
  filter(!(NAME %in% c("P11", "P17", "P22")))

testmerge2 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

testmerge3 <- merge_df %>%
  mutate(
    NAME = str_extract(NAME, "\\d+") %>% as.numeric(),
    unimodal = case_when(
      unimodal %in% c("1", "2") ~ "Unimodal",
      !unimodal %in% c("1", "2") ~ "Self-touch"
    ),
    QUESTION = case_when(
      QUESTION == "t" ~ "Judge Touch",
      QUESTION == "m" ~ "Judge Movement"
    ) %>% factor(levels = c("Judge Touch", "Judge Movement")),
    ACTIVE = case_when(
      ACTIVE == "a" ~ "Active",
      ACTIVE == "p" ~ "Passive"
    ) %>% factor(levels = c("Passive", "Active"))
  ) %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(n = n())

ggplot(testmerge3) +
  geom_point(aes(x = NAME, y = n, color = unimodal)) +
  facet_wrap(QUESTION ~ ACTIVE) +
  scale_x_continuous(limits = c(0, 25), breaks = seq(0, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, by = 18)) +
  scale_color_discrete("Condition") +
  labs(
    title = "Check for data completeness - Before Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )


demogr_df <- read_xlsx(file.path(pathlist$demogr_data_path, "demographic.xlsx"))
merge_df <- left_join(merge_df, demogr_df, by = "NAME")

test <- merge_df %>% filter(is.na(unimodal))
```

```{r Save merged data, warning=FALSE, message=FALSE, echo=FALSE, eval=!preload.data}
# Export merged data to Excel
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
write_xlsx(merge_df, file.path(pathlist$result_path, xlsx_name))
# print(codebookr::codebook(rawData), file.path(pathlist$result_path,"ST_EEG_Codebook.docx"))

rm(list = c(
  "demogr_df",
  "beh_combined_df", "beh_test",
  "eeg_combined_df", "eeg_test",
  "empty_row",
  "merge_df",
  ls(pattern = "^test")
))
```


```{r Read from csv, warning=FALSE, message=FALSE, echo=FALSE}
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
# xlsx_name <- "BEH_EEG_Data_21112025.xlsx"
source(file.path(function_path, "preprocessdata.R"))
# channels <- expand.grid(c("F", "Fc", "FC", "C", "CP", "P"), c("3", "5", "z", "4", "6"))
channels <- expand.grid(c("C"), c("3", "4"))
channels <- paste0(channels$Var1, channels$Var2)
```

**Target Length**: based on the task type (touchLength or movLength is selected).

**Gain/Flipped Gain**: 1 = Unity (move=touch), 2 = NonUnity, incl Move > Touch and Move < Touch.

**Condition Labels (condN)**: (1) Self-touch Active - Judge Touch, 
(2) Self-touch Passive - Judge Touch, 
(3) Self-touch Active - Judge Move, 
(4) Self-touch Passive - Judge Move*, 
(5) Unimodal - Judge Touch, 
(6) Unimodal Active - Judge Move, 
(7) Unimodal Passive - Judge Move. 

**Flipped Gain**: Calculated as $|\frac{TargetLength}{InterferenceLength}\ |$.        **Absolute Error**: Calculated as $|\frac{ReportedLength}{TargetLength}\ - 1|$.

```{r Preprocess data, layout="l-body-outset", fig.width=4, fig.height=4, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
options(width = 500)

rawData <- read_excel(path = file.path(pathlist$result_path, xlsx_name))
rawData <- preprocess_beh_df(rawData) %>%
  select(
    sbjN, Gender, trialN, task, mov, unimodal, condN, BLOCK, trial_number, DURATION, MovDur, HalfDur,
    gain, flipped.gain, touchLength, movLength, Target_length, Interference_length, resp, estError, absError, delta,
    starts_with(channels)
  )

rawData %>%
  select(
    sbjN, condN, BLOCK, trialN, flipped.gain, Target_length, Interference_length, resp,
    matches("^(C3|C4).*_(pre|full|early|late)$")
  ) %>%
  arrange(sbjN, condN, BLOCK, trialN) %>%
  rmarkdown::paged_table(options = list(rows.print = 5, cols.print = 10))
```


# Removing outliers

## Beh: Extreme Responses

Hardware error: Participants might press hard on the keyboard key and immediately submitted the answer, causing this key to be depressed (mechanical sticking) and return extreme responses which did not reflect participant’s actual perception. We used a global filter to remove trials where estimation error exceeded the 1.5×IQR. 


```{r Filter extreme responses, fig.width=12, fig.height=5, echo=TRUE, warning=FALSE, message=FALSE}
# Make long data
filter.choice <- list(
  "puffer", # extreme responses across all participants
  "sbjN" # extreme responses of each participant
)

rawData.filter <- filter_outliers(
  df = rawData %>% mutate(puffer = 1 %>% as.factor()),
  value_col = "estError", group_cols = filter.choice[[1]]
) # filter extreme response
ggplot(rawData) +
  geom_histogram(aes(x = 100 * estError)) +
  scale_x_continuous("Estimation Error (%)", limits = c(-150, 300)) +
  labs(title = "Response distribution before filtering out outliers")
ggplot(rawData.filter) +
  geom_histogram(aes(x = 100 * estError)) +
  scale_x_continuous("Estimation Error (%)", limits = c(-150, 300)) +
  labs(title = "Response distribution after filtering out outliers")

# --- Calculate Data Loss ---
# Print summary
cat(sprintf(
  "%d/%d trials removed: %.2f%%\n",
  nrow(rawData) - nrow(rawData.filter),
  nrow(rawData),
  100 * (nrow(rawData) - nrow(rawData.filter)) / nrow(rawData)
))

# Identify which conditions are losing the most data
(loss_report <- rawData %>%
  anti_join(rawData.filter, by = c("sbjN", "condN", "BLOCK", "trial_number")) %>%
  count(condN, name = "excluded_count"))

```


## EEG: Extreme Beta power values

We filter extremes and Log transform the skewed Beta power values at each channel and movement phase

```{r Filter extreme beta power values, fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
longrawData <- long_beh_eeg_df(rawData.filter)
ggplot(longrawData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5, position = "identity") +
  facet_wrap(~timing) +
  scale_x_continuous(expression(paste("Beta Power (", mV^2, ")"))) +
  # scale_y_continuous(limits = c(0, 2000)) +
  labs(title = "Distribution of Raw Beta Power before filtering out outliers")

filter.choice <- list(
  "puffer", # extreme responses across all participants
  "sbjN", # extreme responses of each participant
  c("sbjN", "channellocation_timing"), # filter extreme Beta power values by participant and electrode position and timing
  "channellocation_timing"
)
# filtering outliers
longData <- filter_outliers(df = longrawData, value_col = "powerBeta", group_cols = filter.choice[[4]])
ggplot(longData) +
  geom_histogram(aes(x = powerBeta, fill = location), alpha = .5, position = "identity") +
  facet_wrap(~timing) +
  scale_x_continuous(expression(paste("Beta Power", "(", mV^2, ")"))) +
  # scale_y_continuous(limits = c(0, 2000)) +
  labs(title = "Distribution of Raw Beta Power after filtering out outliers")

# log-transform

if (power.type == "log") {
  longData <- longData %>%
    mutate(across(starts_with(c("powerBeta")), ~ 10 * log10(.x))) # log-transformation for raw beta power in each channel

  ggplot(longData) +
    geom_histogram(aes(x = powerBeta, fill = location), alpha = .5, position = "identity") +
    facet_wrap(~timing) +
    scale_x_continuous(expression(paste("Beta Power (dB)"))) +
    # scale_y_continuous(limits = c(0, 2000)) +
    labs(title = "Distribution of Log-Transformed Beta Power after filtering out outliers")
}


shortData <- short_beh_eeg_df(longData %>% select(sbjN:powerBeta)) %>%
  mutate(unimodal = as.factor(unimodal))

# QQplot
shortData <- shortData%>%
         mutate(PowerDiff = case_when(task == "Judge Touch" ~C4_full-C3_full,
                                      task == "Judge Movement"  ~C3_full-C4_full)
                )
ggplot(shortData, 
    aes(sample = PowerDiff)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  labs(title = "Beta Power Difference: Normal Q-Q Plot before log10 transformation")
# shapiro.test(shortData$PowerDiff)
# 'pnorm' tells the test to compare data against a normal distribution
ks.test(shortData$PowerDiff %>% na.omit(), 
        "pnorm", 
        mean(shortData$PowerDiff %>% na.omit()), 
        sd(shortData$PowerDiff %>% na.omit()))

# --- Calculate Data Loss ---
# Identify which conditions are losing the most data
(loss_report <- rawData.filter %>%
  anti_join(shortData, by = c("sbjN", "trial_number", "condN", "BLOCK")) %>%
  count(sbjN,condN, BLOCK,trial_number, name = "excluded_count"))

cat(sprintf(
  "%d/%d trials removed: %.2f%%\n",
  sum(loss_report$excluded_count),
  nrow(rawData.filter),
  100 * sum(loss_report$excluded_count) / nrow(rawData.filter)
))


# To calculate change of Beta power
# present data frame in one column for C3, one column for C4
parData <- longData %>%
  select(sbjN:delta, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

if (Target.interference.analysis) {
  parData <- parData %>%
    mutate(PowerDiff = case_when(task == "Judge Touch" ~ C4-C3,
                               task == "Judge Movement"  ~ C3-C4))
}

if (power.type == "log_of_difference") {
  parData <- parData %>%
    mutate(PowerDiff = log10(PowerDiff))
}
  
### Check for normal distribution ----
ggplot(parData) +
  geom_histogram(aes(x = PowerDiff), alpha = .5, position = "identity") +
  facet_wrap(~timing) +
  scale_x_continuous(sprintf("Beta %s", predictor.name)) +
  # scale_y_continuous(limits = c(0, 2000)) +
  labs(title = sprintf("Distribution of Beta %s after filtering out outliers", predictor.name))
# QQplot
ggplot(parData, aes(sample = PowerDiff)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  labs(title = "Beta Power Difference: Normal Q-Q Plot after log10 transformation")
ks.test(parData$PowerDiff %>% na.omit(), 
        "pnorm", 
        mean(parData$PowerDiff %>% na.omit()), 
        sd(parData$PowerDiff %>% na.omit()))

byBaseline.shortData <- shortData %>%
  select(sbjN:absError, starts_with("C3"), starts_with("C4"))



if (power.type == "raw") {
  byBaseline.shortData <- byBaseline.shortData %>%
    rowwise() %>%
    # For raw data:
    mutate(
      C3_full = 100 * (C3_full - C3_pre) / C3_pre,
      C4_full = 100 * (C4_full - C4_pre) / C4_pre,
      C3_early = 100 * (C3_early - C3_pre) / C3_pre,
      C4_early = 100 * (C4_early - C4_pre) / C4_pre,
      C3_late = 100 * (C3_late - C3_pre) / C3_pre,
      C4_late = 100 * (C4_late - C4_pre) / C4_pre
    ) %>%
    mutate(C3_pre = 0, C4_pre = 0)
}

if (power.type == "log") {
  byBaseline.shortData <- byBaseline.shortData %>%
    rowwise() %>%
    # For Decibels (Log) data
    mutate(
      C3_full = (C3_full - C3_pre),
      C4_full = (C4_full - C4_pre),
      C3_early = (C3_early - C3_pre),
      C4_early = (C4_early - C4_pre),
      C3_late = (C3_late - C3_pre),
      C4_late = (C4_late - C4_pre)
    ) %>%
    mutate(C3_pre = 0, C4_pre = 0)
}

byBaseline.longData <- long_beh_eeg_df(byBaseline.shortData)

# Create a unique trial ID in both datasets
longData <- longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

byBaseline.longData <- byBaseline.longData %>%
  mutate(trialID = paste(sbjN, condN, BLOCK, trialN, gain, touchLength, movLength, Target_length, Interference_length, resp, location, timing, sep = "_"))

# Filter byBaseline.longData to keep only rows present in longData - remove outliers based off the raw power Beta
byBaseline.longData <- byBaseline.longData %>%
  filter(trialID %in% longData$trialID)


byBaseline.parData <- byBaseline.longData %>%
  select(sbjN:absError, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff = C3 - C4)

testmerge4 <- shortData %>%
  filter(!is.na(C3_early) & !is.na(C4_early))%>%
  mutate(sbjN = str_extract(sbjN, "\\d+") %>% as.numeric()) %>%
  group_by(sbjN, task, mov, unimodal) %>%
  summarise(n = n()) %>%
  mutate(remain_percent = case_when(
    unimodal == "Self-touch" ~ n / 54,
    unimodal == "Unimodal" ~ n / 36
  ))

ggplot(testmerge4) +
  geom_point(aes(x = sbjN, y = n, color = unimodal)) +
  facet_wrap(task ~ mov) +
  scale_x_continuous(limits = c(1, 25), breaks = seq(1, 24, 1)) +
  scale_y_continuous(limits = c(0, 54), breaks = seq(0, 54, length.out = 5)) +
  scale_color_discrete("Condition") +
  labs(
    title = "Check for data completeness - After Excluding Outliers",
    x = "Participant Number",
    y = "Number of Data"
  )

# rm(list = c(ls(pattern = "raw|test")))
```


```{r Exclude participant with large missing data, fig.width=12, fig.height=5, echo=TRUE, warning=FALSE, message=FALSE}
# Early phase
exclude = c("P01","P06","P10", "P14") # we have no cut-off to exclude particants with large NaNs 
exclude = c()

```

# Participants
```{r Demographics, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Sex distribution
shortData %>%
  distinct(sbjN, Gender) %>%
  group_by(Gender) %>%
  summarise(n = n()) %>%
  mutate(per = n / sum(n)) %>%
  ggplot() +
  geom_col(aes(x = Gender, y = 100 * per, fill = Gender), show.legend = F) +
  labs(
    title = "Participant - Sex",
    x = "Sex", y = "Percentage (%)"
  ) +
  theme(
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )
```


# Behavioral results

```{r Behavioral Plots, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# Subject-level aggregation
plotData <- shortData %>%
  group_by(sbjN, task, mov, unimodal, gain, Target_length) %>%
  summarise(response = mean(resp), .groups = "drop") %>%
  group_by(task, mov, unimodal, gain, Target_length) %>%
  summarise(
    mean = mean(response),
    se = sd(response) / sqrt(n()), # SE across subjects
    n = n(),
    .groups = "drop"
  )

# Plot
p1 <- ggplot(data = plotData %>% filter(unimodal == "Self-touch")) +
  geom_point(aes(x = Target_length, y = mean, color = gain), show.legend = F) +
  geom_line(aes(x = Target_length, y = mean, color = gain, group = gain), show.legend = F) +
  geom_ribbon(aes(
    x = Target_length, ymin = mean - se, ymax = mean + se,
    fill = gain, group = gain
  ), alpha = 0.15, show.legend = F) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(task ~ mov) +
  scale_x_continuous(limits = c(2, 10), breaks = seq(4, 8, by = 2)) +
  scale_y_continuous(limits = c(2, 10), breaks = seq(2, 10, by = 2)) +
  scale_color_manual(values = c("#DD6B20", "#667dff", "#00ab7c")) +
  scale_fill_manual(values = c("#DD6B20", "#667dff", "#00ab7c")) +
  labs(
    title = "Self-touch Conditions",
    x = "Actual target extent (cm)", y = "",
    color = "Gain", fill = "Gain"
  ) +
  theme(
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16)
  )

p2 <- ggplot(data = plotData %>% filter(unimodal == "Unimodal")) +
  geom_point(aes(x = Target_length, y = mean, color = gain), show.legend = T) +
  geom_line(aes(x = Target_length, y = mean, color = gain, group = gain), show.legend = T) +
  geom_ribbon(aes(
    x = Target_length, ymin = mean - se, ymax = mean + se,
    fill = gain, group = gain
  ), alpha = 0.15, show.legend = T) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(task ~ mov, drop = T) +
  scale_x_continuous(limits = c(2, 10), breaks = seq(4, 8, by = 2)) +
  scale_y_continuous(limits = c(2, 10), breaks = seq(2, 10, by = 2)) +
  scale_color_manual(values = c("#DD6B20", "#667dff", "#00ab7c")) +
  scale_fill_manual(values = c("#DD6B20", "#667dff", "#00ab7c")) +
  labs(
    title = "Unimodal Conditions",
    x = "Actual target extent (cm)", y = "Perceived target extent (cm)",
    color = "Gain", fill = "Gain"
  ) +
  theme(
    legend.position = c(.15, .9),
    aspect.ratio = 1,
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.key = element_blank(),
    legend.background = element_rect(fill = "transparent"),
    legend.title = element_text(size = 16)
  )

grid.arrange(p2, p1, ncol = 2)
```

## Calculate Interference Coefficients
```{r ICs, fig.height= 7, fig.width= 7, warning=FALSE, message=FALSE, collapse = TRUE}
w <- shortData %>%
  filter(unimodal == "Self-touch") %>%
  # filter(gain != 1.25, gain != 0.8)  %>%
  group_by(sbjN, mov, task) %>%
  do({
    model <- lm(resp ~ 0 + touchLength + movLength, data = .)
    as.data.frame(t(coef(model)))
  }) %>%
  ungroup() %>%
  mutate(
    normTouch = touchLength / (movLength + touchLength),
    normMove = movLength / (movLength + touchLength),
    weights = case_when(
      task == "Judge Touch" ~ normMove,
      task == "Judge Movement" ~ normTouch
    )
  )

w$mov <- factor(w$mov, levels = c("Active", "Passive"))

wideW <- w %>%
  select(-c(touchLength, movLength, normTouch, normMove)) %>%
  pivot_wider(
    names_from = c(task, mov), # Columns to use for names
    values_from = c(weights), # Values to fill in the table
    names_sep = "_"
  )
# clipr::write_clip(wideW)

ggplot(w, aes(x = mov, y = weights, fill = interaction(mov, task))) +
  geom_bar(stat = "summary", show.legend = FALSE) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  facet_wrap(~task) +
  ylim(0, 1) +
  labs(
    x = "Condition",
    y = "Weigt of task-irrelevant information (ω)",
    title = "Mean Interference Weights (ω) \nAcross Movement and Judgment Conditions"
  ) +
  theme(
    aspect.ratio = 2,
    legend.position = "bottom",
    strip.text = element_text(size = 10),
    plot.title = element_text(size = 13),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12)
  )
```

## Run ANOVA
```{r Behavioral ANOVA, warning=FALSE, message=FALSE, collapse = TRUE}
full_ANOVA <- aov_ez(
  id = "sbjN",
  dv = "weights",
  within = c("mov", "task"),
  data = w,
  anova_table = list(correction = "GG", es = "pes") # request partial eta squared
)

# Use nice() to display the ANOVA table with effect sizes:
nice(full_ANOVA)
```



## Self-touch: asymmetry index by conditions
**Main effect of movement type**: Active movement causes stronger beta desynchronization in left hemisphere (C3)

**Main effect of task**: Judging movement is associated with lower beta in left hemisphere (C3; negative asymmetry index), judging touch is associated with lower beta in right hemisphere (C4; positive asymmetry index)

**Main effect of gain**: One relatively larger modality is associated with lower beta in the corresponding hemisphere. Larger movement is associated with lower beta in left hemisphere, larger touch is associated with lower beta in right hemisphere.



### Unity vs NonUnity:


```{r Prepare for ANOVA1, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 

# 1. Filter for EARLY movement (first ~1 second) and prep variables
filter.timing <- "Early"

predictData <- parData %>%
  filter(unimodal == "Self-touch" & timing == paste(filter.timing, "Movement")) %>%
  filter(!is.na(PowerDiff)) %>%
  mutate(sbjN = factor(sbjN)) %>%
  mutate(gain = case_when(gain == "Move = Touch" ~ "2Unity",
                          gain != "Move = Touch" ~ "1NonUnity"))

# 2. Pre-aggregate: Calculate both Mean and Median per participant/cell
subj_data <- predictData %>%
  group_by(sbjN, mov, task, gain) %>%
  summarise(
    mean_PowerDiff = mean(PowerDiff, na.rm = TRUE),
    median_PowerDiff = median(PowerDiff, na.rm = TRUE),
    trial_count = n(), # Good practice: keep track of how many trials made up this average
    .groups = "drop"
  )

# 3. Run the ANOVA on the MEANS
power_anova_mean <- aov_ez(
  id = "sbjN",                           
  dv = "mean_PowerDiff", # Using the pre-calculated mean                    
  within = c("mov", "task", "gain"),     
  data = subj_data,
  anova_table = list(correction = "GG", es = "pes") 
)

print("ANOVA using MEAN Beta Asymmetry:")
nice(power_anova_mean)

# 4. (Optional) Run the ANOVA on the MEDIANS for a robustness check
power_anova_median <- aov_ez(
  id = "sbjN",                           
  dv = "median_PowerDiff", # Using the pre-calculated median                    
  within = c("mov", "task", "gain"),     
  data = subj_data,
  anova_table = list(correction = "GG", es = "pes") 
)

print("ANOVA using MEDIAN Beta Asymmetry:")
nice(power_anova_median)



```

```{r Posthoc1, fig.width=10, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# 1. Post-Hoc for the Significant mov:gain Interaction (p = .024)
# Option A: Look at the effect of 'mov' at each level of 'gain'
emm_mov_by_gain <- emmeans(power_anova_mean, ~ mov | gain)

cat("\n--- Estimated Marginal Means: mov by gain ---\n")
print(emm_mov_by_gain)

cat("\n--- Pairwise Comparisons: differences in 'mov' within each 'gain' ---\n")
# Using "holm" adjustment for multiple comparisons (standard and powerful)
pairs(emm_mov_by_gain, adjust = "holm")


# Option B: Look at the effect of 'gain' at each level of 'mov'
emm_gain_by_mov <- emmeans(power_anova_mean, ~ gain | mov)

cat("\n--- Pairwise Comparisons: differences in 'gain' within each 'mov' ---\n")
pairs(emm_gain_by_mov, adjust = "holm")



# 2. Main Effect of Task (p < .001)

# Since df = 1 (meaning there are only 2 levels of task), the p-value for the 
# pairwise comparison will match your ANOVA. This step is primarily to extract 
# the estimated marginal means so you know which task had a higher/lower PowerDiff.

emm_task <- emmeans(power_anova_mean, ~ task)

cat("\n--- Estimated Marginal Means: Task ---\n")
print(emm_task)

cat("\n--- Pairwise Comparisons: Task ---\n")
pairs(emm_task)
```


```{r Plot1a, fig.width=10, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 

# Calculate group-level data for plotting (using the subj_data you already made)
plot_data <- subj_data %>%
  group_by(mov, task, gain) %>%
  summarise(
    group_mean = mean(mean_PowerDiff, na.rm = TRUE),
    sd = sd(mean_PowerDiff, na.rm = TRUE),
    n = sum(!is.na(mean_PowerDiff)),
    se = sd / sqrt(n),
    .groups = "drop"
  )

# Plot the 3-Way Interaction
pAnova <- ggplot(plot_data, aes(x = mov, y = group_mean, color = gain, group = gain)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_point(size = 3, position = position_dodge(width = 0.3)) +
  geom_line(size = 1, position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = group_mean - se, ymax = group_mean + se), 
                width = 0.2, size = 0.8, position = position_dodge(width = 0.3)) +
  
  # Helper text
  annotate("text", x = 1.5, y = Inf, label = paste("↑", positive.label), 
           vjust = 2, color = "gray30", fontface = "italic", size = 4) +
  annotate("text", x = 1.5, y = -Inf, label = paste("↓", negative.label), 
           vjust = -1, color = "gray30", fontface = "italic", size = 4) +
  
  scale_color_manual(values = c("#DD6B20", "#667dff", "#00ab7c")) +
  
  # Facet by Task to see the 3-way split
  facet_wrap(~ task) +
  
  labs(
    title = paste(filter.timing, "Movement: 3-Way Interaction on Beta Asymmetry"),
    subtitle = "How Movement, Task, and Gain interact to shift interhemispheric asymmetry index",
    x = "Movement Type",
    y = "Mean Beta Power Difference (C3 - C4)",
    color = "Gain"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    strip.text = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.position = "bottom"
  )

pAnova

```



```{r Plot1b, fig.width=10, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 

# 2. Pre-aggregate: Calculate both Mean and Median per participant/cell
subj_data <- predictData %>%
  group_by(sbjN, mov, gain) %>%
  summarise(
    mean_PowerDiff = mean(PowerDiff, na.rm = TRUE),
    median_PowerDiff = median(PowerDiff, na.rm = TRUE),
    trial_count = n(), # Good practice: keep track of how many trials made up this average
    .groups = "drop"
  )

# Calculate group-level data for plotting (using the subj_data you already made)
plot_data <- subj_data %>%
  group_by(mov, gain) %>%
  summarise(
    group_mean = mean(mean_PowerDiff, na.rm = TRUE),
    sd = sd(mean_PowerDiff, na.rm = TRUE),
    n = sum(!is.na(mean_PowerDiff)),
    se = sd / sqrt(n),
    .groups = "drop"
  )

# Plot the 3-Way Interaction
pAnova <- ggplot(plot_data, aes(x = mov, y = group_mean, color = gain, group = gain)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_point(size = 3, position = position_dodge(width = 0.3)) +
  geom_line(size = 1, position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = group_mean - se, ymax = group_mean + se), 
                width = 0.2, size = 0.8, position = position_dodge(width = 0.3)) +
  
  scale_color_manual(values = c("#f64559", "#667dff", "#00ab7c")) +
  
  # Helper text
  annotate("text", x = 1.5, y = Inf, label = "↑ Tactile Focus (C3 > C4)", 
           vjust = 2, color = "gray30", fontface = "italic", size = 4) +
  annotate("text", x = 1.5, y = -Inf, label = "↓ Motor Focus (C4 > C3)", 
           vjust = -1, color = "gray30", fontface = "italic", size = 4) +
  
  labs(
    title = "Early Movement: 2-Way Interaction on Beta Asymmetry",
    subtitle = "How Movement and Gain interact to shift interhemispheric asymmetry index",
    x = "Movement Type",
    y = "Mean Beta Power Difference (C3 - C4)",
    color = "Gain"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    strip.text = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.position = "bottom"
  )

pAnova

```

### Three gains:


```{r Prepare for ANOVA, fig.width=16, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 

# 1. Filter for EARLY movement (first ~1 second) and prep variables
filter.timing <- "Early"

predictData <- parData %>%
  filter(unimodal == "Self-touch" & timing == paste(filter.timing, "Movement")) %>%
  filter(!is.na(PowerDiff)) %>%
  mutate(sbjN = factor(sbjN)) %>%
  mutate(gain = factor(gain, levels = c("Move < Touch", 
                                        "Move = Touch", 
                                        "Move > Touch"), 
                       label = c("Move < Touch", "Move = Touch", "Move > Touch")
                       # label = c("LargerTouch", "Congruent", "LargerMove")
                       )) # %>%
  # mutate(gain = factor(flipped.gain, levels = c("Target < Interference", "1.Unity", "Target > Interference"), label = c("LargerInterference", "MatchingInformation", "SmallerInterference")))

# 2. Pre-aggregate: Calculate both Mean and Median per participant/cell
subj_data <- predictData %>%
  group_by(sbjN, mov, task, gain) %>%
  summarise(
    mean_PowerDiff = mean(PowerDiff, na.rm = TRUE),
    median_PowerDiff = median(PowerDiff, na.rm = TRUE),
    trial_count = n(), # Good practice: keep track of how many trials made up this average
    .groups = "drop"
  )

# 3. Run the ANOVA on the MEANS
power_anova_mean <- aov_ez(
  id = "sbjN",                           
  dv = "mean_PowerDiff", # Using the pre-calculated mean                    
  within = c("mov", "task", "gain"),     
  data = subj_data,
  anova_table = list(correction = "GG", es = "pes") 
)

print("ANOVA using MEAN Beta Asymmetry:")
nice(power_anova_mean)

# 4. (Optional) Run the ANOVA on the MEDIANS for a robustness check
power_anova_median <- aov_ez(
  id = "sbjN",                           
  dv = "median_PowerDiff", # Using the pre-calculated median                    
  within = c("mov", "task", "gain"),     
  data = subj_data,
  anova_table = list(correction = "GG", es = "pes") 
)

print("ANOVA using MEDIAN Beta Asymmetry:")
nice(power_anova_median)



```


```{r Posthoc, fig.width=10, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 
# 1. Post-Hoc for the Significant mov:gain Interaction (p = .024)
# Option A: Look at the effect of 'mov' at each level of 'gain'
emm_mov_by_gain <- emmeans(power_anova_mean, ~ mov | gain)

cat("\n--- Estimated Marginal Means: mov by gain ---\n")
print(emm_mov_by_gain)

cat("\n--- Pairwise Comparisons: differences in 'mov' within each 'gain' ---\n")
# Using "holm" adjustment for multiple comparisons (standard and powerful)
pairs(emm_mov_by_gain, adjust = "holm")


# Option B: Look at the effect of 'gain' at each level of 'mov'
emm_gain_by_mov <- emmeans(power_anova_mean, ~ gain | mov)

cat("\n--- Pairwise Comparisons: differences in 'gain' within each 'mov' ---\n")
pairs(emm_gain_by_mov, adjust = "holm")



# 2. Main Effect of Task (p < .001)

# Since df = 1 (meaning there are only 2 levels of task), the p-value for the 
# pairwise comparison will match your ANOVA. This step is primarily to extract 
# the estimated marginal means so you know which task had a higher/lower PowerDiff.

emm_task <- emmeans(power_anova_mean, ~ task)

cat("\n--- Estimated Marginal Means: Task ---\n")
print(emm_task)

cat("\n--- Pairwise Comparisons: Task ---\n")
pairs(emm_task)
```

```{r Plota, fig.width=10, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 

# Calculate group-level data for plotting (using the subj_data you already made)
plot_data <- subj_data %>%
  group_by(mov, task, gain) %>%
  summarise(
    group_mean = mean(mean_PowerDiff, na.rm = TRUE),
    sd = sd(mean_PowerDiff, na.rm = TRUE),
    n = sum(!is.na(mean_PowerDiff)),
    se = sd / sqrt(n),
    .groups = "drop"
  )

# Plot the 3-Way Interaction
pAnova <- ggplot(plot_data, aes(x = mov, y = group_mean, color = gain, group = gain)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_point(size = 3, position = position_dodge(width = 0.3)) +
  geom_line(size = 1, position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = group_mean - se, ymax = group_mean + se), 
                width = 0.2, size = 0.8, position = position_dodge(width = 0.3)) +
  
  scale_color_manual(values = c("#DD6B20", "#667dff", "#00ab7c")) +
  
  # Helper text
  annotate("text", x = 1.5, y = Inf, label = "↑ Tactile Focus (C3 > C4)", 
           vjust = 2, color = "gray30", fontface = "italic", size = 4) +
  annotate("text", x = 1.5, y = -Inf, label = "↓ Motor Focus (C4 > C3)", 
           vjust = -1, color = "gray30", fontface = "italic", size = 4) +
  
  # Facet by Task to see the 3-way split
  facet_wrap(~ task) +
  
  labs(
    title = paste(filter.timing, "Movement: 3-Way Interaction on Beta Asymmetry"),
    subtitle = "How Movement, Task, and Gain interact to shift interhemispheric asymmetry index",
    x = "Movement Type",
    y = "Mean Beta Power Difference (C3 - C4)",
    color = "Gain"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    strip.text = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.position = "bottom"
  )

pAnova

```

```{r Plotb, fig.width=10, fig.height=10, echo=TRUE, warning=FALSE, message=FALSE} 

# 2. Pre-aggregate: Calculate both Mean and Median per participant/cell
subj_data <- predictData %>%
  group_by(sbjN, mov, gain) %>%
  summarise(
    mean_PowerDiff = mean(PowerDiff, na.rm = TRUE),
    median_PowerDiff = median(PowerDiff, na.rm = TRUE),
    trial_count = n(), # Good practice: keep track of how many trials made up this average
    .groups = "drop"
  )

# Calculate group-level data for plotting (using the subj_data you already made)
plot_data <- subj_data %>%
  group_by(mov, gain) %>%
  summarise(
    group_mean = mean(mean_PowerDiff, na.rm = TRUE),
    sd = sd(mean_PowerDiff, na.rm = TRUE),
    n = sum(!is.na(mean_PowerDiff)),
    se = sd / sqrt(n),
    .groups = "drop"
  )

# Plot the 3-Way Interaction
pAnova <- ggplot(plot_data, aes(x = mov, y = group_mean, color = gain, group = gain)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_point(size = 3, position = position_dodge(width = 0.3)) +
  geom_line(size = 1, position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = group_mean - se, ymax = group_mean + se), 
                width = 0.2, size = 0.8, position = position_dodge(width = 0.3)) +
  
  scale_color_manual(values = c("#DD6B20", "#667dff", "#00ab7c")) +
  
  # Helper text
  annotate("text", x = 1.5, y = Inf, label = "↑ Tactile Focus (C3 > C4)", 
           vjust = 2, color = "gray30", fontface = "italic", size = 4) +
  annotate("text", x = 1.5, y = -Inf, label = "↓ Motor Focus (C4 > C3)", 
           vjust = -1, color = "gray30", fontface = "italic", size = 4) +
  
  labs(
    title = "Early Movement: 2-Way Interaction on Beta Asymmetry",
    subtitle = "How Movement and Gain interact to shift interhemispheric asymmetry index",
    x = "Movement Type",
    y = "Mean Beta Power Difference (C3 - C4)",
    color = "Gain"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    strip.text = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.position = "bottom"
  )

pAnova

```

