---
title: "TOUCH-BRAIN: Pre-Registration Plan"
author: "Phuc TU Nguyen"
date: "2025-06-06"

output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    toc: true
    toc_depth: 3
    number_sections: true
    collapse: true
---

```{r setup, warning=FALSE, echo=FALSE, message=FALSE}
## Set up libraries and define paths

rm(list = ls())
library(rstudioapi)

script_path <- dirname(rstudioapi::getActiveDocumentContext()$path)
function_path <- file.path(script_path, "function")

source(file.path(function_path, "loadconfig.R"))
load_lib()
load_path(script_path)
load_palette()

phases <- c("Movement Cue", "Before Movement", "Early Movement", "Half Movement", "Late Movement", "After Movement")
vps <- c("P")
```


# Pool data {.hidden .unlisted}
<font size="1"> Behavioral and EEG data are merged across all participants and blocks. Block number and trial number are assigned per condition (t/m &times; a/p &times; unimodal/both) </font>

```{r warning=FALSE, message=FALSE, echo=FALSE}
source(file.path(function_path, "loaddata.R"))

# BEH ----
beh_combined_df <- load_behdata(vps, pathlist$beh_data_path)
beh_combined_df <- adjust_beh_df(beh_combined_df)
# Test for sufficient blocks
beh_test <- beh_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial_beh = n(), .groups = "drop")

# EEG ----
eeg_combined_df <- load_eegdata(vps, pathlist$eeg_data_path)

# Adjustment according to protocol
{
  empty_row <- eeg_combined_df[1, ]
  empty_row[1, ] <- NA

  empty_row$filename <- "P23_move_active_results.xls"
  eeg_combined_df <- rbind(eeg_combined_df[1:(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[36]), ], 
                           empty_row, 
                           eeg_combined_df[(which(eeg_combined_df$filename == "P23_move_active_results.xlsx")[37]):nrow(eeg_combined_df), ])
  eeg_combined_df <- eeg_combined_df[-which(eeg_combined_df$filename == "P23_move_passive_results.xlsx")[51], ]
}


eeg_combined_df <- adjust_eeg_df(eeg_combined_df)

# Test for sufficient blocks
eeg_test <- eeg_combined_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal) %>%
  summarise(ntrial = n(), .groups = "drop")

# Compare trial counts between behavioral and EEG data
testmerge <- left_join(beh_test, eeg_test,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal")
) %>%
  arrange(NAME, unimodal, QUESTION, ACTIVE) %>%
  mutate(trialdiff = ntrial_beh - ntrial)

```

```{r warning=FALSE, message=FALSE, echo=FALSE}
# Merge full behavioral and EEG datasets
merge_df <- left_join(beh_combined_df, eeg_combined_df,
  by = c("NAME", "QUESTION", "ACTIVE", "unimodal", "trial_number")
)

testmerge1 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal)%>%
  summarise(n = n())
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
# Remove specific blocks for specific subjects

# pilot004: OK
# pilot005: [unimodal1_m_a Block 1 and 3] - exclude VP
# pilot006: [t_a block 3]
# pilot007: [m_a block 2] [t_p block 2] and ?
# pilot008: [m_p block 1]
# pilot009: [unimodal1_m_p block 1]
# pilot010: OK
# pilot011: OK
# pilot012: OK


merge_df <- merge_df %>%
  filter(!(NAME == "pilot005" & is.na(unimodal) & QUESTION == "t" & ACTIVE == "a")) %>%
  filter(!(NAME == "pilot005" & is.na(unimodal) & QUESTION == "m" & ACTIVE == "a")) %>%
  filter(!(NAME == "pilot006" & is.na(unimodal) & QUESTION == "t" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "pilot007" & is.na(unimodal) & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(2))) %>%
  filter(!(NAME == "pilot007" & is.na(unimodal) & QUESTION == "t" & ACTIVE == "p" & BLOCK %in% c(2))) %>%
  filter(!(NAME == "pilot008" & is.na(unimodal) & QUESTION == "m" & ACTIVE == "p" & BLOCK %in% c(1))) %>%
  filter(!(NAME == "pilot009" & unimodal == "1" & QUESTION == "m" & ACTIVE == "p" & BLOCK %in% c(1))) %>%
  filter(!(NAME == "P03" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "p" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P17" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P22" & is.na(unimodal) & unimodal == NA & QUESTION == "t" & ACTIVE == "a" & BLOCK %in% c(3))) %>%
  filter(!(NAME == "P23" & is.na(unimodal) & unimodal == NA & QUESTION == "m" & ACTIVE == "p" & trial_number %in% c(50))) %>%
  filter(!(NAME == "P25" & !is.na(unimodal) & unimodal == "1" & QUESTION == "m" & ACTIVE == "a" & BLOCK %in% c(1))) %>%
  # temporary filter due to unsatisfactory preprocessing
  filter(!(NAME %in% c("P11","P17","P22") )) 

testmerge2 <- merge_df %>%
  group_by(NAME, QUESTION, ACTIVE, unimodal)%>%
  summarise(n = n())

```

```{r warning=FALSE, message=FALSE, echo=FALSE}
# Export merged data to Excel
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
write_xlsx(merge_df, file.path(pathlist$result_path, xlsx_name))
```


## Load and preprocess raw data 
```{r warning=FALSE, message=FALSE, echo=FALSE}
xlsx_name <- format(Sys.time(), "BEH_EEG_Data_%d%m%Y.xlsx")
source(file.path(function_path, "preprocessdata.R"))
# channels <- expand.grid(c("F", "Fc", "FC", "C", "CP", "P"), c("3", "5", "z", "4", "6"))
channels <- expand.grid(c("C"), c("3", "4"))
channels <- paste0(channels$Var1, channels$Var2)
```

**Target Length**: based on the task type (touchLength or movLength is selected).

**Condition Labels (condN)**: (1) Self-touch Active - Judge Touch, 
(2) Self-touch Passive - Judge Touch, 
(3) Self-touch Active - Judge Move, 
(4) Self-touch Passive - Judge Move*, 
(5) Unimodal - Judge Touch, 
(6) Unimodal Active - Judge Move, 
(7) Unimodal Passive - Judge Move. 

**Flipped Gain**: Calculated as $|\frac{TargetLength}{InterferenceLength}\ |$.

**Absolute Error**: Calculated as $|\frac{ReportedLength}{TargetLength}\ - 1|$.

```{r layout="l-body-outset", fig.width=4, fig.height=4, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
rawData <- read_excel(path = file.path(pathlist$result_path, xlsx_name))
rawData <- preprocess_beh_df(rawData) %>%
  select(
    sbjN, trialN, task, mov, unimodal, condN, BLOCK, trial_number,
    gain, flipped.gain, touchLength, movLength, Target_length, Interference_length, resp, estError, absError, delta,
    starts_with(channels)
  )

# Check number of trials per blk per ppt per phase
test <- rawData %>% count(sbjN, condN)

rawData %>%
  select(sbjN, condN, BLOCK, trialN, flipped.gain, Target_length, resp, 
         C3_movcue, C4_movcue, C3_pre, C4_pre, C3_early, C4_early, C3_half, C4_half, C3_late, C4_late, C3_post, C4_post) %>%
  arrange(sbjN, condN, BLOCK, trialN) %>%
  rmarkdown::paged_table(options = list(rows.print = 10, cols.print = 9))
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
# EEG ----
# Make long data

longrawData <- long_beh_eeg_df(rawData)

longData <- filter_outliers(df = longrawData, value_col = "powerBeta", group_cols = c("channellocation_timing"))

longData <- filter_outliers(df = longData %>% mutate(puffer=1%>%as.factor()), value_col = "resp", group_cols = c("puffer"))%>%
  mutate(flipped.gain=factor(flipped.gain, labels = c("Target<Non-Target", "Target=Non-Target", "Target>Non-Target")),
         gain=factor(gain, labels = c("Move < Touch", "Move = Touch", "Move > Touch")))
longData$resp %>% hist()

shortData <- short_beh_eeg_df(longData %>% select(sbjN:powerBeta)) %>%
  mutate(unimodal = as.factor(unimodal))


parData <- longData %>%
  select(sbjN:delta, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta)%>%
  mutate(PowerDiff=C3-C4)

# %Change of Beta power
byBaseline.shortData <- shortData %>%
  select(sbjN:absError, starts_with("C3"), starts_with("C4")) %>%
  rowwise() %>%
  mutate(
    C3_movcue = 100 * (C3_movcue - C3_pre) / C3_pre,
    C4_movcue = 100 * (C4_movcue - C4_pre) / C4_pre,
    C3_early = 100 * (C3_early - C3_pre) / C3_pre,
    C4_early = 100 * (C4_early - C4_pre) / C4_pre,
    C3_half = 100 * (C3_half - C3_pre) / C3_pre,
    C4_half = 100 * (C4_half - C4_pre) / C4_pre,
    C3_late = 100 * (C3_late - C3_pre) / C3_pre,
    C4_late = 100 * (C4_late - C4_pre) / C4_pre,
    C3_post = 100 * (C3_post - C3_pre) / C3_pre,
    C4_post = 100 * (C4_post - C4_pre) / C4_pre
  ) %>%
  mutate(C3_pre = 0, C4_pre = 0)


byBaseline.longData <- long_beh_eeg_df(byBaseline.shortData)

byBaseline.parData <- byBaseline.longData %>%
  select(sbjN:absError, location, timing, powerBeta) %>%
  pivot_wider(names_from = location, values_from = powerBeta) %>%
  mutate(PowerDiff=C3-C4)
```


# Research questions
```{r fig.width=14, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
source(file.path(function_path, "reformvariable.R"))

aveData <- ave_df(rawData)
wide.aveData <- ave_wide_df(aveData)

ggplot(aveData, aes(x = Target_length, y = response, color = factor(gain), group = gain)) +
  geom_point(stat = "summary", size = 2) +
  geom_line(stat = "summary", size = 1, show.legend = FALSE) +
  stat_summary(fun.data = "mean_se", geom = "ribbon", aes(fill = factor(gain)), alpha = 0.2, show.legend = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  facet_grid(unimodal ~ task + mov) + # Organize by subject (rows) and hand/task/mov (columns)
  ylim(2, 14) +
  scale_y_continuous(breaks = seq(2, 12, by = 2)) + # Set y-axis ticks at intervals of 2
  xlim(2, 10) +
  labs(x = "Actual target extent (cm)", y = "Perceived target extent (cm)", color = "Gain") +
  scale_color_manual(values = palette$three.color1) +
  scale_fill_manual(values = palette$three.color1) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
```

## Replication: Asymmetric bidirectional interference and Active movement
We will replicate the asymmetrical bidirectional interference of movement and tactical spatial percepts in Cataldo et al. (2022):
<p style="text-align: justify;">
**Q1: During self-touch, is there an asymmetric interference of movement and touch on tactile and motor spatial percepts, respectively?**

H1: The interference coefficients (ICs) of task-irrelevant information are significantly larger when participants judge touch compared to movement.
</p>

<p style="text-align: justify;">
**Q2: During self-touch, is the asymmetric interference during self-touch larger in active movement than in passive movement?**

H2: ICs are significantly larger when participants are in active movement conditions than in passive movement conditions.**
</p>

**Q3: Does interference occur when either motor or tactile information is available?**

H3: ICs are significantly larger than 0 (zero) in self-touch conditions but not unimodal conditions.
</p>

<center style="color:#15925E;">**ICs across conditions**</center>

```{r fig.width=14, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
w <- weight_df(shortData)
wide.w <- weight_wide_df(w)

ggplot(w, aes(x = condN, y = weights, fill = condN)) +
  geom_bar(stat = "summary", show.legend = FALSE) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  facet_wrap(~unimodal, scale = "free_x") +
  ylim(0, 1) +
  xlab("Condition") +
  ylab("Weigth of task-irrelevant information (ω)") +
  scale_fill_manual(values = palette$eight.color) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 13),
    axis.title = element_text(size = 18)
  )
```



## Neural marker for motor and tactile processing

Beta ERD *(i.e., a decrease in beta band power)* over contralateral motor cortex is observed before and Early Movement, while beta ERS *(i.e., a subsequent increase in power)* occurs after movement completion (Doyle et al., 2005; Stolk et al., 2019). Beta suppression at central scalp sites is also associated with long touch (Von Mohr et al., 2018) and typically reported in the contralateral somatosensory cortex (Singh et al., 2014; Valenza et al., 2018). We will replicate the results that beta power is reduced Early Movement and touch in the contralateral EEG channel position (C3 and C4, respectively) to reflect the processing of relevant information during unimodal tasks. 

<p style="text-align: justify;">
**Q4: (Unimodal conditions) Is beta power in the contralateral channel, i.e., C3 and C4, Early Movement and touch a neural marker for the processing of motor and tactile spatial information, respectively?**

H4: Beta power Early Movement and touch is lower than pre-movement (i.e., larger ERD) in the contralateral channel and less so in the ipsilateral channel.
</p>

<center style="color:#15925E;">**Is beta power in the contralateral channel Early Movement/touch a neural marker for the processing of motor/tactile spatial information?**</center>
```{r fig.width=15, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
# EEG ----
plotData <- longData %>%
  filter(timing %in% phases &
           unimodal == "Unimodal" & !is.na(relativehemisphere) & location %in% c("C3", "C4")) %>%
  group_by(timing, condN, relativehemisphere, location) %>%
  get_summary_stats(powerBeta, show = c("ci", "mean", "sd"))

ggplot(plotData) +
  # geom_col(aes(x = condN, y = mean, group = timing, fill = timing) , position = "dodge")+
  geom_point(aes(x = timing, y = mean, color = condN)) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), linewidth = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), width = .3) +
  geom_text(
    data = plotData %>% filter(timing == "Movement Cue"),
    aes(x = timing, y = mean + mean * runif(6, min = -0.01, max = 0.03), label = location, color = condN),
    position = position_nudge(x = -0.3)
  ) +
  labs(
    title = "",
    x = "Timing",
    y = expression(Averaged ~ beta ~ Power ~ (mV^2))
  ) +
  scale_color_manual("Condition", values = palette$three.color2) +
  scale_fill_manual("Condition", values = palette$three.color2) +
  facet_wrap(~relativehemisphere) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 15),
    axis.text.x = element_text(angle = 15),
    axis.title = element_text(size = 18)
  )
```

<center style="color:#15925E;">**Is there ERD Early Movement and touch?**</center>

*Note*. This plot is placeholder only. This is not continuous data. Phuc will check back the latency.

```{r fig.width=15, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
# EEG: ERD normalized ----

plotData <- byBaseline.longData %>%
  filter(timing %in% phases & unimodal == "Unimodal" & !is.na(relativehemisphere) & location %in% c("C3", "C4")) %>%
  group_by(timing, condN, relativehemisphere, location) %>%
  get_summary_stats(powerBeta, show = c("ci", "mean", "sd"))

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN)) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), linewidth = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), width = .3) +
  # geom_text(data = plotData %>% filter(timing == "After Movement"),
  #           aes(x = timing, y = mean + mean * runif(6, min = -0.5, max = .51), label = location, color = condN),
  #           position = position_nudge(x = 0.3))+
  labs(
    title = "",
    x = "Timing",
    y = "Power change (%)"
  ) +
  scale_color_manual("Condition", values = palette$three.color2) +
  scale_fill_manual("Condition", values = palette$three.color2) +
  facet_wrap(~relativehemisphere) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 15),
    axis.text.x = element_text(angle = 15),
    axis.title = element_text(size = 18)
  )
```


<center style="color:#15925E;">**Does self-touch cause beta ERD? At which hemisphere and electrodes?**</center>


```{r fig.width=15, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
plotData <- longData %>%
  filter(timing %in% phases & unimodal == "Self-touch" & !is.na(relativehemisphere)) %>%
  group_by(timing, condN, relativehemisphere) %>%
  get_summary_stats(powerBeta, show = c("ci", "mean", "sd"))

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN)) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), linewidth = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), width = .3) +
  labs(
    title = "",
    x = "Hemisphere",
    y = expression(Average ~ beta ~ Power ~ (mV^2))
  ) +
  scale_color_manual("Condition", values = palette$four.color1) +
  scale_fill_manual("Condition", values = palette$four.color1) +
  facet_wrap(~relativehemisphere) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 15),
    axis.text.x = element_text(angle = 15),
    axis.title = element_text(size = 18)
  )
```

<center style="color:#15925E;">**Is there ERD Early Movement and touch?**</center>

*Note*. This plot is placeholder only because it does not visualize continuous data. Phuc will check the latency.

```{r fig.width=15, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE}
# EEG: ERD normalized ----

plotData <- byBaseline.longData %>%
  filter(timing %in% phases & unimodal == "Self-touch" & !is.na(relativehemisphere) & location %in% c("C3", "C4")) %>%
  group_by(timing, condN, relativehemisphere, location) %>%
  get_summary_stats(powerBeta, show = c("ci", "mean", "sd"))

ggplot(plotData) +
  geom_point(aes(x = timing, y = mean, color = condN)) +
  geom_line(aes(x = timing, y = mean, color = condN, group = condN), linewidth = 3) +
  geom_errorbar(aes(x = timing, ymin = mean - ci, ymax = mean + ci, color = condN), width = .3) +
  # geom_text(data = plotData %>% filter(timing == "After Movement"),
  #           aes(x = timing, y = mean + mean * runif(6, min = -0.5, max = .51), label = location, color = condN),
  #           position = position_nudge(x = 0.3))+
  labs(
    title = "",
    x = "Timing",
    y = "Power change (%)"
  ) +
  scale_color_manual("Condition", values = palette$four.color1) +
  scale_fill_manual("Condition", values = palette$four.color1) +
  facet_wrap(~relativehemisphere) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 15),
    axis.text.x = element_text(angle = 15),
    axis.title = element_text(size = 18)
  )
```

## Unimodal: Beta power for predicting motor/tactile percepts

<p style="text-align: justify;">
**Q5: Beta power Early Movement in contralateral channels could be associated with judgement of the length of movement and touch**

H5: Larger beta power in the contralateral channel Early Movement predicts smaller normalized absolute errors in judgement.
</p>

*Note* that normalized absolute error does not consider the direction of estimation (over/underestimate).

<center style="color:#15925E;">**Using Lower beta power at early movement/touch for predicting judgement error**</center>
```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
plotData <- longData %>%
  filter(timing == "Early Movement" & unimodal == "Unimodal" & hemisphere != "mid" & location %in% c("C3", "C4"))

label_data <- plotData %>%
  group_by(condN, relativehemisphere, location) %>%
  filter(powerBeta == min(powerBeta)) %>%
  ungroup()

ggplot(
  plotData,
  aes(x = powerBeta, y = absError, color = condN)
) +
  geom_point(alpha = .1) +
  geom_smooth(method = "lm") +
  geom_text(
    data = label_data,
    aes(x = min(plotData$powerBeta), label = location),
    position = position_nudge(x = -0.05),
    show.legend = FALSE
  ) +
  facet_wrap(~relativehemisphere) +
  scale_color_manual("Condition", values = palette$three.color2) +
  labs(
    # title = "Beta Power at the Beginning and the End of the Experiment",
    x = expression(beta ~ Power ~ (mV^2)),
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 15),
    axis.title = element_text(size = 18)
  )
```


## Self-touch: Interhemispheric interference
### Basic analyses

  - **Normalized Absolute Error** quantifies *perceptual interference*, i.e., the degree to which the perceptual judgement deviates from the true value OR how much the perceptual judgement is interfered by other information.
  
  $$Perceptual Inference = |1-\frac{reported length}{true length}\ |$$
  
  - **Beta Power Difference** between the left hemisphere (C3) and the right hemisphere (C4) represents the degree to which motor activity interferes with tactile processing. Positive difference implies weaker interference of motor information (tactile focus), while negative difference implies stronger interference of motor information (motor focus).
  
  $$\Delta{B} = B_{C3} - B_{C4}$$
  
  - **Beta Power Sum** of the left hemisphere (C3) and the right hemisphere (C4) represents the global beta power that implies participants' wakefulness. Lower global beta power is associated with increased wakefulness
  
  $$\sum{B} = B_{C3} + B_{C4}$$
  

Because movement and tactile spatial percepts during self-touch are interfered by the processing of tactile and movement information, respectively, we expect that the neural marker of these two components could be used to predict judgement accuracy. For example, a negative difference in beta power between C3 and C4 *(C3 - C4)* reflects larger processing of motor information relative to tactile information and may suggest that motor information is weighted more in length judgement than tactile judgement

<p style="text-align: justify;">

**Q6: (Self-touch conditions) Does the relative difference in beta power between channel C3 and C4 during self-touch explain the asymmetrical, bidirectional interference of movement and tactile spatial percepts?**

H6: Negative difference in the beta power between the channels C3 and C4 [C3-C4] (i.e., stronger motor processing than tactile processing) is associated with smaller error in move judgement and smaller tactile judgement.


-----------------------------------------------------------------------
New part

```{r fig.width=16, fig.height=15, echo=FALSE, warning=FALSE, message=FALSE} 
# Raw Beta power ---------------
# Absolute error 

plotData <- parData %>% filter(unimodal == "Self-touch" & gain != "Move = Touch")

ggplot(plotData,
       aes(x = PowerDiff, y = absError, color = task)) +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = F) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power",
    x = "Beta Power Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(mov~timing, nrow=2) +
  theme(
    # legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- parData %>%
  filter(unimodal == "Self-touch" & gain != "Move = Touch" & timing %in% c("Early Movement")) %>% 
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```

```{r fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}

plotData <- parData %>% filter(unimodal == "Self-touch" & mov == "Active")

ggplot(plotData,
       aes(x = PowerDiff, y = estError, color = task)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F)+
  geom_smooth(method = "lm", show.legend = F) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Active Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-6.5, 5.5))+
  scale_y_continuous(limits = c(-1, 2.5))+
  facet_wrap(gain~timing, nrow = 3) +
  theme(
    # legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- parData %>%
  filter(gain != "Move = Touch" & unimodal == "Self-touch"  & timing %in% c("Early Movement")) %>% 
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov * gain+ (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=16, fig.height=15, echo=FALSE, warning=FALSE, message=FALSE}
# %change Beta power -------
# Absolute error

plotData <- byBaseline.parData %>% filter(unimodal == "Self-touch" & gain != "Move = Touch")

ggplot(plotData,
       aes(x = PowerDiff, y = absError, color = task)) +
  geom_point(alpha = .05, show.legend = F) +
  geom_smooth(method = "lm", show.legend = F) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Predicting with the relative degree of ERD",
    x = "Beta ERD Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(mov~timing, nrow=2) +
  theme(
    # legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- byBaseline.parData %>%
  filter(unimodal == "Self-touch" & gain != "Move = Touch" & timing %in% c("Early Movement")) %>% 
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=12, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}

plotData <- byBaseline.parData %>% filter(unimodal == "Self-touch" & mov == "Passive")

ggplot(plotData,
       aes(x = PowerDiff, y = estError, color = task)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(alpha = .05, show.legend = F)+
  geom_smooth(method = "lm", show.legend = F) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power (Passive Conditions)",
    x = "Beta Power Difference: C3 - C4",
    y = "Judgement Error\n(both Over and Underestimation)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  scale_x_continuous(limits = c(-755, 600))+
  scale_y_continuous(limits = c(-1, 2.5))+
  facet_wrap(gain~timing, nrow = 3) +
  theme(
    # legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- parData %>%
  filter(unimodal == "Self-touch"  & timing %in% c("Early Movement") & gain != "Move = Touch") %>% 
  mutate(sbjN = factor(sbjN))

# Fit the linear mixed model
model <- lmer(estError ~ PowerDiff * task * mov * gain+ (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


-----------------------------------------------------------------------
</p>
<center style="color:#15925E;">**Beta power difference for predicting judgement error**</center>

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# PRE-MOVEMENT ----
plotData <- shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1)

ggplot(
  plotData,
  aes(x = C3_pre - C4_pre, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(flipped.gain ~ mov) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power \nin Pre-Movement",
    x = "Beta Power Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
predictData <- shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1) %>%
  mutate(
    PowerDiff = C3_pre - C4_pre,
    sbjN = factor(sbjN)
  )

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# EARLY-MOVEMENT ----
plotData <- shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1)

ggplot(
  plotData,
  aes(x = C3_early - C4_early, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ mov) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power \nin Early Movement",
    x = "Beta Power Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1) %>%
  mutate(
    PowerDiff = C3_early - C4_early,
    sbjN = factor(sbjN)
  )

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
plotData <- byBaseline.shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1)

ggplot(
  plotData,
  aes(x = C3_early - C4_early, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(flipped.gain ~ mov) +
  labs(
    title = "Predicting with the difference of ERD \nin Early Movement",
    x = "Beta ERD Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
```


```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# HALF-MOVEMENT ----
## Raw beta ----
plotData <- shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1)

ggplot(
  plotData,
  aes(x = C3_half - C4_half, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(flipped.gain ~ mov) +
  labs(
    title = "Predicting Judgement Error with Difference of Beta Power \nin half Movement",
    x = "Beta Power Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1) %>%
  mutate(
    PowerDiff = C3_half - C4_half,
    sbjN = factor(sbjN)
  )

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
## Beta change ----
plotData <- byBaseline.shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1)

ggplot(
  plotData,
  aes(x = C3_half - C4_half, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(flipped.gain ~ mov) +
  labs(
    title = "Predicting with the difference of ERD \nin half Movement",
    x = "Beta ERD Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
# LATE-MOVEMENT ----
plotData <- shortData %>%
  filter(unimodal == "Self-touch")

ggplot(
  plotData,
  aes(x = C3_late - C4_late, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~mov) +
  labs(
    title = "Predicting with Difference of Beta Power \nin Late Movement",
    x = "Beta Power Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )

predictData <- shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1) %>%
  mutate(
    PowerDiff = C3_late - C4_late,
    sbjN = factor(sbjN)
  )

# Fit the linear mixed model
model <- lmer(absError ~ PowerDiff * task * mov + (1 | sbjN), data = predictData)

# View the summary of the model
summary(model)
```


```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
plotData <- byBaseline.shortData %>%
  filter(unimodal == "Self-touch" & flipped.gain != 1)

ggplot(
  plotData,
  aes(x = C3_late - C4_late, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(flipped.gain ~ mov) +
  labs(
    title = "Predicting with the difference of ERD \nin Late Movement",
    x = "Beta ERD Difference: C3 - C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
```

## Self-touch: Control for participant's wakefulness

A decrease in beta power in both hemisphere during tactile stimulation is observed when individuals are alert (Illman et al., 2021).

<p style="text-align: justify;">
**Q7: (Self-touch conditions) Does the sum in beta power in channels C3 and C4 Early Movement explain the movement and tactile spatial percepts regardless of task and movement type?**

H7: Smaller sum of beta power in channels C3 and C4 [C3+C4] (i.e., higher alert state) is associated with smaller error in touch judgement and larger error in move judgement.
</p>

<center style="color:#15925E;">**Sum of beta power for predicting judgement error**</center>

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
plotData <- shortData %>%
  filter(unimodal == "Self-touch")

ggplot(
  plotData,
  aes(x = C3_early + C4_early, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  facet_wrap(~mov) +
  labs(
    title = "Sum in Beta Power During Early Movement",
    x = "Beta Power Sum: C3 + C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
plotData <- shortData %>%
  filter(unimodal == "Self-touch")

ggplot(
  plotData,
  aes(x = C3_late + C4_late, y = absError, color = task)
) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm") +
  facet_wrap(~mov) +
  labs(
    title = "Sum in Beta Power During Late Movement",
    x = "Beta Power Sum: C3 + C4",
    y = "Perceptual Interference \n(Normalized Absolute Error)"
  ) +
  scale_color_manual("Task", values = palette$two.color1) +
  facet_wrap(~mov) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),
    plot.title = element_text(size = 19),
    axis.text = element_text(size = 18),
    axis.title = element_text(size = 18)
  )
```

### Additional analyses: Error by Gain
